---
title: "Untitled"
author: "Jonathan Bourne"
date: "13/09/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script is used to create and save the IEEE networks into a usable R format that can be smoothly integrated with the powergridnetworking pacakge.

The IEEE networks are loaded from matpower format using the PES power grid library. https://github.com/power-grid-lib props to them for doing all the hard work of gathering and standardising.

```{r}
packages <- c("tidyverse", "igraph","readr","readxl", "ggraph")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

select <- dplyr::select
arrange <- dplyr::arrange
sapply(packages, library, character.only = TRUE)

library(PowerGridNetworking)
library(NetworkSpringEmbedding)
```


```{r}
IEEE_data_folder <- file.path(basewd, "IEEE power flow data")
Project_folder <- "/home/jonno/Dropbox/IEEE_Networks" #/media/jonno/Seagate Expansion Drive/IEEE_Networks"
IEEE_networks <- file.path(Project_folder, "IEEE_network_files")

```


Data in common format from
http://labs.ece.uw.edu/pstca/
https://egriddata.org/dataset/ieee-30-bus-power-flow-test-case


A useful paper for cyber physical references and stufff to do with power grids. Electrical Engineer friendly
-Cyber-Physical Models for Power Grid Security Analysis: 8-Substation Case 

#Matpower version

explanation of the matpower case format can be found here
https://matpower.org/docs/ref/matpower5.0/caseformat.html

```{r}

the_ieee_test_cases <- list.files("/home/jonno/pglib-opf-master", pattern = "ieee.m", full.names = TRUE)

the_ieee_test_cases



c(14, 30, 57, 118, 300) %>% walk(~{
  
  
  mat_dat <- matpower_loader(the_ieee_test_cases[which.max(grepl(.x, the_ieee_test_cases))], output_graph = F)
  
  bus_data <- mat_dat$bus %>%
    select(bus = bus_i, demand = Pd, generation = Pmax) %>%
    mutate(net_generation = generation - demand,
           Name = bus)
  
  branch_data <- mat_dat$branch %>% #mutate(b1 = 1/x)
    select(fbus, tbus, Y = x ) %>%
    mutate(Y = 1/Y, #simplification for DC power flow assumptions
           edge_name = paste(fbus, tbus, sep = "-")) %>% #name the links
    group_by(fbus, tbus, edge_name) %>%
    #Remove parallel lines summing the susceptances
    summarise(
      Y = sum(Y)) %>% ungroup
  
  
  g<- graph_from_data_frame(branch_data, directed = F, vertices = bus_data)
  
  g <-  BalencedGenDem(g, 
                       Demand = "demand",
                       Generation = "generation",
                       OutputVar = "net_generation")
  
  SlackRef <- SlackRefFunc(g, name = "name", Generation = "generation")
  
  g <- PowerFlow(g, SlackRef = SlackRef$name, EdgeName ="edge_name", VertexName = "name", Net_generation = "net_generation", power_flow = "power_flow")
  
  saveRDS(g, file = file.path(power_grid_graphs_path , paste0("IEEE_", .x, "_igraph.rds")))
  
})

```



#Plot 118

```{r}

  IEEE_number <- 300

g <- read_rds(file.path(power_grid_graphs_path , paste0("IEEE_", IEEE_number, "_igraph.rds")))

AZero <- CreateTransmission(g,  EdgeName ="edge_name", VertexName = "name")
LineProperties <- LinePropertiesMatrix(g = g,  Edgename ="edge_name", Weight = "Y")

g<- g%>%
  PowerFlow(., AZero = AZero, LineProperties = LineProperties, EdgeName ="edge_name", VertexName = "name", Net_generation = "net_generation", power_flow = "power_flow")



#uses ggraph!
set.seed(158)
ggraph(g, layout = layout_with_fr(g)) +
   geom_edge_link2(aes(colour = abs(power_flow)), width = 0.7) +
  scale_edge_colour_viridis() +
  geom_node_point( aes(shape =  case_when(net_generation ==0 ~"Transmission",
                                        net_generation > 0 ~"Generation",
                                        TRUE ~"Demand")),
                   size = 2.5) +
  labs(edge_colour = "Power flow", shape = "Node type", "") +
  ggtitle("IEEE 118 power grid with Fruchtman Reingold projection")
ggsave(file.path(Figures_path, "IEEE_118_fr_proj.pdf"))

```

#Convert UK high voltage
This chunk re-creates the UK high voltage network as a standardised network with the same properties and names as the IEEE network.
This just makes the network more interchangeable with the other networks and so smoothes the coding.
```{r}
#The base directory called by the sourced script
basewd <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder"
source(file.path("/home/jonno/ProportionalLoading", "CreateGBase.R"))

test <- as_data_frame(gbase)

UK_edges <- gbase %>% as_data_frame() %>%
  rename(power_flow = PowerFlow, 
         edge_name = Link, 
         edge_capacity = Link.Limit) %>%
  select(from, to, edge_name, Y, power_flow, edge_capacity)

UK_vertices <- gbase %>% as_data_frame(., what = "vertices") %>%
  rename(demand = Demand, generation = Generation, net_generation = BalencedPower ) %>%
  mutate(Name = name) %>%
  select(-Bus.Order,
         -component,
         -Voltage)

UK_standard <- graph_from_data_frame(UK_edges, directed = FALSE, vertices = UK_vertices)

saveRDS(UK_standard, file = file.path(power_grid_graphs_path , paste0("UK_high_voltage", ".rds")))

```

#Create a topological network
This creates a small 4 cliq and 3 cliq network joined by a single edge. This network is for testing purposes
```{r}
test_g <- bind_rows(expand.grid(LETTERS[1:4],LETTERS[1:4]),
expand.grid(LETTERS[5:7],LETTERS[5:7]),
tibble(Var1 = "D", Var2 = "E")) %>%
  filter(Var1 != Var2) %>%
  mutate(power_flow = 1, #these are just to allow easy swap in and out with the IEEE graph. should be changed
         edge_capacity = 2,
         distance = 1,
         k = 500,
         edge_name = paste(Var1, Var2, sep ="_")) %>%
  graph_from_data_frame(., directed = F) %>%
set_vertex_attr(., name = "net_generation", value = (betweenness(.) -mean(betweenness(.))))


as_data_frame(test_g)

test_g%>%
  plot()
```

