---
title: "Untitled"
author: "Jonathan Bourne"
date: "29 April 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---


This code needs to be run after the SytemDynamics set up chunk

```{r}
IEEE_data_folder <- file.path(basewd, "IEEE power flow data")
Project_folder <- "/media/jonno/Seagate Expansion Drive/IEEE_Networks"
IEEE_networks <- file.path(Project_folder, "IEEE_network_files")

```


#Create the network
```{r}
test <- read_delim(file = file.path(IEEE_data_folder, "ieee118cdf.txt"),
                       delim = " ",
                       #skip = 2,
                       col_names = FALSE)

#each file is broken up into cards which represent different parts of the network
#The first two cards are nodes and edges respectively. At the end of each of the main cards the number -999 is shown.
#The final -999 is the end of the file followby by a single text line.

card_end <- read_delim(file = file.path(IEEE_data_folder, "ieee118cdf.txt"),
                       delim = " ",
                       col_names = FALSE) %>% 
  pull(1) %>% 
  {. =="-999"} %>% 
  which

skip <- 2
nodes <- read_delim(file = file.path(IEEE_data_folder, "ieee118cdf.txt"),
                       delim = " ",
                       skip = skip,
                       col_names = FALSE,
                                       trim_ws = TRUE,
                   n_max = card_end[1]-1-skip) %>%
  set_names(c("Bus_Number", "Name", "Area_Number", "drop", "Loss_zone", "Type" , "final_voltage_pu", "final_angle_degs", "Load_MW", "LOAD_MVAR", "Generation_MW", "Generation_MVAR", "Base_KV", "Desired_volts_pu", "Max_MVAR", "Min_MVAR", "Conductance", "Susceptance", "Remote_controlled_Bus_number" )) 

#A couple of node names appear twice, so I use the Bus number as the official name of the node
#This causes issues to do with the edge name
test <- nodes %>%
  group_by(Bus_Number, Name) %>%
  summarise(counts = n()) %>%
  group_by(Name) %>%
  summarise(counts = n()) %>%
  filter(counts>1)

skip <- card_end[1]+1
edges <- read_delim(file = file.path(IEEE_data_folder, "ieee118cdf.txt"),
                   delim = " ",
                   skip = skip,
                   col_names = FALSE,
                   trim_ws = TRUE,
                   n_max = card_end[2]-1-skip) %>%
  set_names(c("Tap_bus_number", "Z_bus_number", "Load_flow_area", "Loss_zone", "Circuit", "Type", "Branch_resistance_R_pr_unit", "Branch_resistance_X_pr_unit", "Line_charging_B_pr_unit", "Line_MVA rating_No_1", "Line_MVA_rating_No_2", "Line_MVA_rating_No_3", "Control_bus_number", "Side", "Transformer_final_turns_ratio", "Transformer_final_angle", "Minimum_tap_phase_shift", "Maximum_tap_phase_shift", "Step_size", "Minimum_voltage", "Maximum_voltage"))


#The edges with near zero variance are unused anyway so I can drop them without issues
edges2 <- edges %>%
  mutate(Y = 1/Branch_resistance_X_pr_unit) %>%#We are using the DC assumuptions and the value of R is small compared to X thus we can say susceptance B = 1/X
  rename(from = Tap_bus_number, to = Z_bus_number) %>%
  select(-nearZeroVar(.),-Branch_resistance_R_pr_unit,-Branch_resistance_X_pr_unit) %>%
  left_join(select(nodes, from = Bus_Number, Name), by = "from")%>%
  left_join(select(nodes, to = Bus_Number, Name), by = "to") %>%
  mutate(Link = paste(Name.x, Name.y, sep = "-")) %>%
  select(-Name.x,-Name.y) %>%
  group_by(from, to) %>%
  #Remove parallel lines summing the susceptances
  summarise(Y = sum(Y),
            Link = first(Link)) 
  

  nodes2 <-nodes %>% select(-nearZeroVar(.)) %>%
      #A substantial amount of the generation is negative aka load, I move it into the load column
    mutate(
      Load_MW = if_else( Generation_MW<0,Load_MW-Generation_MW, Load_MW),
      Generation_MW = if_else(Generation_MW<0, 0, Generation_MW),
      Net_Generation = Generation_MW - Load_MW)


IEEE_118 <- graph_from_data_frame(edges2, vertices = nodes2, directed = FALSE)

#The forces need balancing
IEEE_118 <-  BalencedGenDem(IEEE_118, 
                   Demand = "Load_MW",
                   Generation = "Generation_MW",
                   OutputVar = "Net_Generation")

SlackRef <- SlackRefFunc(IEEE_118, name = "name", Generation = "Generation_MW")

IEEE_118 <- PowerFlow(IEEE_118, SlackRef$name, EdgeName ="Link", VertexName = "name", Net_generation = "Net_Generation")

saveRDS(IEEE_118, file = file.path(IEEE_networks, "IEEE_118_igraph.rds"))
    
```


#Plot 118

```{r}
test2 <- as_data_frame(IEEE_118) %>%
  mutate(absPF = abs(PowerFlow),
         rank = rank(absPF))


NodePosition <- test2 %>%
  select(from, to, Link, PowerFlow) %>%
  gather(key = type, value = Node, -Link, -PowerFlow)

 set.seed(158)
  BaseCoords <- layout_with_fr(IEEE_118) %>% 
    as_tibble %>% 
    mutate(Node = names(V(IEEE_118))) %>%
    rename(Longitude = V1,
           Latitude = V2) %>%
    left_join(NodePosition, .) %>%
    left_join(nodes2 %>% 
                select(Node = Bus_Number, Name, Net_Generation) %>% 
                mutate(Node = as.character(Node),
                       Node_type = case_when(Net_Generation ==0 ~"Transmission",
                                        Net_Generation > 0 ~"Generation",
                                        TRUE ~"Demand")), .)

  BaseCoords %>%
  ggplot(aes(x = Longitude, y = Latitude, group = Link)) + geom_line() +  
    geom_point(aes(shape = Node_type, colour = Node_type))
  
    BaseCoords %>%
  ggplot(aes(x = Longitude, y = Latitude, group = Link, colour = abs(PowerFlow))) + geom_line() +  
    geom_point(aes(shape = Node_type), size = 2) +
    scale_color_viridis_c()

```


#PL attack IEEE118
##Edges
```{r}

IEEE_118 <- readRDS(file = file.path(IEEE_networks, "IEEE_118_igraph.rds"))
setwd(file.path(Project_folder, "IEEE118_edges"))

rep <-5
alpha_vector <- c(1, 1.02, 1.01, 1.005, 1.05, 1.1, 1.2, 1.5, 2, 3, 5, 7, 10, 15, 20, 50, 100, 200, Inf)
alpha_vector
set.seed(21256)
DeleteOrders_Edges <- MultiAttackOrder(IEEE_118, Target ="Edges", Sims = 100, Name = "Link")  

#Create the simulations for each of the alpha avalues using 100 simulations for each
alpha_vector %>% walk(~{
  gProp <- Proportional_Load(IEEE_118, alpha = .x)
  
  folder <- paste0("alpha_value_",  .x*100)
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  CascadeMode <- ifelse(is.finite(.x), TRUE, FALSE)
  
  SaveMultiAttacks(gProp, DeleteOrders_Edges, folder, 
                   TotalAttackRounds = 1000, 
                   CascadeMode = CascadeMode,
                   Demand = "Load_MW",
                   Generation = "Generation_MW",
                   EdgeName = "Link", 
                   VertexName = "name", 
                   Net_generation = "Net_Generation",
                   Target = "Edges")
  
}

)



```

##Nodes
```{r}
set.seed(21256)
DeleteOrders_Nodes <- MultiAttackOrder(IEEE_118, Sims = 100)  

#The vector of alpha values to be tested
alpha_vector <- c(1, 1.02, 1.01, 1.005, 1.05, 1.1, 1.2, 1.5, 2, 3, 5, 7, 10, 15, 20, 50, 100, 200, Inf)
setwd(file.path(Project_folder, "IEEE118_nodes"))

#Create the simulations for each of the alpha avalues using 100 simulations for each
alpha_vector %>% walk(~{
  gProp <- Proportional_Load(IEEE_118, alpha = .x)
  
  folder <- paste0("alpha_value_",  .x*100)
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  SaveMultiAttacks(gProp, DeleteOrders, folder, 
                   TotalAttackRounds = 1000, 
                   CascadeMode = TRUE,
                   Demand = "Load_MW",
                   Generation = "Generation_MW",
                   EdgeName = "Link", 
                   VertexName = "name", 
                   Net_generation = "Net_Generation")
  
}

)


```

#Target orders

Create the target orders for the scrambled edge values
##ec values to attack
```{r}
Scramble_ec_values <- c(1.005, 1.01, 1.05, 1.1, 1.2, 1.5, 2, 3, 5, 7, 10, 20, 100) 
```


```{r}

if(!file.exists(file.path(Project_folder, "target_orders.rds"))){
  
  set.seed(123)
  random_seeds <- sample(1:100000, 10000)
  
  target_orders <- Scramble_ec_values %>% map_df(~{
    
    print(.x)
    #create network
    Scrambled_edge_cap <-  Proportional_Load(IEEE_118, alpha = .x)
    #permute edges
    print("creating the random permutations")
    seed_alpha <- Permute_excess_capacity(Scrambled_edge_cap, random_seeds)
    #take subselection
    target_orders <- sub_selection_of_seed_alpha(seed_alpha, total_samples = 10, seed = 123) %>%
      mutate(ec = .x,
             v = 1:n())
    
    return(target_orders)
    
  })
  
  saveRDS(target_orders, file.path(Project_folder, "target_orders.rds"))
  
} else {
  
  target_orders  <- readRDS(file.path(Project_folder, "target_orders.rds"))
  
}

```

#Fixed EC multi-attack

##Node attack
```{r}
Scramble_ec_values %>% walk(~{
  
  target_orders_x<- target_orders %>% 
    filter(ec == .x)
  
  folder <- paste0("alpha_value_",  .x*100) %>%
    file.path(Project_folder, "IEEE_permute_edge_ec_Node", .)
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  #attack network using the deletion orders
  setwd(folder)
  #create network
  Scrambled_edge_cap <-  Proportional_Load(IEEE_118, alpha = .x)
  #attack!
  Scrambled_Edge_SaveMultiAttacks(target_orders_x, Scrambled_edge_cap, "constant_ec_v", DeleteOrders_Nodes)
  
})
```

##Edge attack
```{r}
IEEE_118<- readRDS(file = file.path(IEEE_networks, "IEEE_118_igraph.rds"))

set.seed(21256)
DeleteOrders <- MultiAttackOrder(IEEE_118, Target ="Edges", Sims = 100, Name = "Link")  
Scramble_ec_values %>% walk(~{
  
  target_orders_x <- target_orders %>% 
    filter(ec == .x)
  
  folder <- paste0("alpha_value_",  .x*100) %>%
    file.path(Project_folder, "IEEE_permute_edge_ec_Edge", .)
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  #attack network using the deletion orders
  setwd(folder)
  #create network
  Scrambled_edge_cap <-  Proportional_Load(IEEE_118, alpha = .x)
  #attack!
  Scrambled_Edge_SaveMultiAttacks(target_orders_x, Scrambled_edge_cap, "constant_ec_v", DeleteOrders_Edges, Target = "Edges")
  
})

```


#calculate strain of the selected networks


The below chunk was put in due to simulations being run with different parameters resulting in out of synch heights. The common values will be used for both the proportionally loaded edges and the ec scrambled edges
```{r}
common_time <- 0.03
common_Iter <- 20000
common_tol <- 1e-10
common_mass <- 1
```


##Propoortionally loaded angles

```{r}
IEEE_Project_folder <- "/media/jonno/Seagate Expansion Drive/IEEE_Networks"

IEEE_118 <- readRDS(file.path(IEEE_Project_folder,"IEEE_network_files", "IEEE_118_igraph.rds"))



#Network loadings to find the angles for
alpha_vector <- c(1, 1.02, 1.01, 1.005, 1.05, 1.1, 1.2, 1.5, 2, 2.5, 3, 5, 7, 10, 15, 20, 50, 100, 200, Inf)

#calculate theta for all values of alpha
alpha_vector %>% walk(~{
  
  alpha <- .x
  
  print(paste("alpha value", alpha))
  
  current_graph  <- IEEE_118 %>%
    Proportional_Load(., alpha = alpha) %>% 
    set.edge.attribute(. , "distance", value = 1) %>%
    Calc_Spring_Youngs_Modulus(., "PowerFlow", "Link.Limit", minimum_value = 100, stretch_range = 1000) %>%
    set.edge.attribute(., "Area", value = 1) %>%
  Normalize_load(., EdgeName = Link, VertexName = name, Net_Generation = Net_Generation, capacity = Link.Limit)
  

  List_of_BiConComps <- Create_balanced_blocks(current_graph, force = "Net_Generation")

    giant_componant <-List_of_BiConComps %>% map_dbl(~vcount(.x)) %>% which.max()
    
  #use the largest block to set the simulation parameters k and m.
  #k needs to be sufficiently stretch to allow enough topology variation. otherwise all that happens is a surface angled in the direct of net power flow. Which is interesting but not that interesting
      OriginBlock_complete <- Find_network_balance(g = List_of_BiConComps[[giant_componant]], 
                                                   force ="Net_Generation",
                                                   flow = "PowerFlow",
                                                   distance = "distance",
                                                   capacity = "Link.Limit",
                                                   tstep = common_time, 
                                                   tol = common_tol, 
                                                   maxIter = common_Iter, 
                                                   mass = common_mass)
      
      final_z <- Create_stabilised_blocks(g = current_graph, 
                                          OriginBlock = OriginBlock_complete,
                                          OriginBlock_number = giant_componant, 
                                          force ="Net_Generation",
                                          flow = "PowerFlow",
                                          distance = "distance",
                                          capacity = "Link.Limit",
                                          tstep = common_time, 
                                          tol = common_tol, 
                                          maxIter = common_Iter, 
                                          mass = common_mass)
  
  write_rds(final_z, file.path(IEEE_Project_folder, "Solved_height_networks_norm", paste0("IEEE_118_alpha_", alpha, ".rds")))
})


  test <-OriginBlock$results

test %>% ggplot(aes(x = t, y = z)) + geom_line()

```


##Scrambled edge strain

```{r}

cpu_id <- 2
number_of_cpus <- 2
cpu_vector <- rep(1:number_of_cpus, length.out =length(Scramble_ec_values))
cpu_sims <-(1:length(Scramble_ec_values))[cpu_vector==cpu_id]


  for(n in Scramble_ec_values[cpu_sims]){
  print(n)
  target_orders2 <- target_orders %>% 
    filter(ec == n)
  
  alpha_folder <-  paste0("Solved_height_networks_alpha_", n*100) %>%
    file.path(Project_folder, "constant_ec_from_alpha_norm", .)
  #create folder if it doesn't already exist
  if(!file.exists(alpha_folder)){
    dir.create(alpha_folder)
  }
  
 1:nrow(target_orders2) %>% walk(~{
    
    ID <- .x
    
    print(paste("alpha value", ID))
    #create network
    Scrambled_edge_cap <-  Proportional_Load(IEEE_118, alpha = n)
    
    set.seed(target_orders2$seed[.x])
    ec_order <- sample(1:ecount(Scrambled_edge_cap), ecount(Scrambled_edge_cap) )
    
    temp <- as_data_frame(Scrambled_edge_cap) %>%
      mutate(ec = Link.Limit-abs(PowerFlow), #get excess capacity
             ec2 = ec[ec_order], #change order of excess capacity
             alpha = (abs(PowerFlow)+ec2)/abs(PowerFlow), #calculate alpha
             Link.Limit = abs(PowerFlow)+ec2)#re-order link limit
    
    print(mean(temp$alpha))
    
    current_graph <- Scrambled_edge_cap %>%
      set.edge.attribute(., "Link.Limit", value = temp$Link.Limit) %>% 
      set.edge.attribute(. , "distance", value = 1) %>%
      Calc_Spring_Youngs_Modulus(., "PowerFlow", "Link.Limit", minimum_value = 100, stretch_range = 1000) %>%
      set.edge.attribute(., "Area", value = 1) %>%
  Normalize_load(., EdgeName = Link, VertexName = name, Net_Generation = Net_Generation, capacity = Link.Limit)
    
  List_of_BiConComps <- Create_balanced_blocks(current_graph, force = "Net_Generation")

    giant_componant <-List_of_BiConComps %>% map_dbl(~vcount(.x)) %>% which.max()
    
  #use the largest block to set the simulation parameters k and m.
  #k needs to be sufficiently stretch to allow enough topology variation. otherwise all that happens is a surface angled in the direct of net power flow. Which is interesting but not that interesting
      OriginBlock_complete <- Find_network_balance(g = List_of_BiConComps[[giant_componant]], 
                                                   force ="Net_Generation",
                                                   flow = "PowerFlow",
                                                   distance = "distance",
                                                   capacity = "Link.Limit",
                                                   tstep = common_time, 
                                                   tol = common_tol, 
                                                   maxIter = common_Iter, 
                                                   mass = common_mass)
      
      final_z <- Create_stabilised_blocks(g = current_graph, 
                                          OriginBlock = OriginBlock_complete,
                                          OriginBlock_number = giant_componant, 
                                          force ="Net_Generation",
                                          flow = "PowerFlow",
                                          distance = "distance",
                                          capacity = "Link.Limit",
                                          tstep = common_time, 
                                          tol = common_tol, 
                                          maxIter = common_Iter, 
                                          mass = common_mass)
    
    write_rds(final_z, file.path(alpha_folder, paste0("IEEE_118_v_", ID, ".rds")))
  })
  
}
```

#Strain and quantity

I beleive that strains link to robustness is mediated throught the concentration of demand and generation nodes.
I will test this by doing the following on the largest block of the IEEE 118 network
Using the largest component prevents dead areas of the network and ensures that the all the experiments are topologically identical

5 quantities of generator fraction is used either 17, 12, 8, 4, 1, or a single generator 
20 random samples of each generator level
5 alpha levels 1, 1.5, 2, 5, Inf

This makes 500 different combinations to try + 5 at 100% of all generators

I then 

```{r}

IEEE_118 <- readRDS(file = file.path(IEEE_networks, "IEEE_118_igraph.rds"))

#alpha levels of the concentrator
alpha_conc <- c(1, 1.5, 2, 5, Inf)

List_of_BiConComps <- Create_balanced_blocks(IEEE_118, force = "Net_Generation")

giant_componant <-List_of_BiConComps %>% map_dbl(~vcount(.x)) %>% which.max()

exp_IEEE <- List_of_BiConComps[[giant_componant]]

#In this case the base slack ref will be the largest power consumer
SlackRef_conc <- "59"

#Generate Attack orders
set.seed(21256)
DeleteOrders_Concentrator_Edges <- MultiAttackOrder(exp_IEEE, Target ="Edges", Sims = 100, Name = "Link")  


#get the node id of all the generators
gen_id <- as_data_frame(exp_IEEE, what = "vertices") %>% filter(Generation_MW >0) %>% pull(name) 

#make a df of all combinations of sample size and sample iteration
combs <- expand.grid(x = c(4,8,12), y = 1:20) %>%
  as_tibble 

quant_alpha_comb <- expand.grid(quant = c(17, 12, 8, 4, 1), alpha = alpha_conc) %>%
  as_tibble


active_gen_df <- map2_df(.x  = combs$x, .y = combs$y, ~{
  
  tibble(active_gen_id =  sample(gen_id, .x, replace = FALSE), sample = .y, quant = .x)
  
}) %>%
  bind_rows(tibble(active_gen_id =  gen_id, sample = 1, quant = 17)) %>% #there is only 1 combination of all generators
  bind_rows(tibble(active_gen_id =  gen_id, sample = 1:17, quant = 1)) %>% #there are only 17 for sample size of 1 so this is added on after the others
left_join(quant_alpha_comb,., by = "quant" ) #join so that each specific quant-sample combo is represented at each alpha quant

#the unique simulation combos to be calculated
simulation <-active_gen_df %>% 
  select(-active_gen_id) %>%
  distinct()

cpu_id <- 4
number_of_cpus <- 4
cpu_vector <- rep(1:number_of_cpus, length.out = nrow(simulation))
cpu_sims <-(1:nrow(simulation))[cpu_vector==cpu_id]


cpu_sims %>% walk(~{
  #set the simulation to calculate
  current_sim <- simulation %>%
    slice(.x)
  
  #folder name is 
  folder <- file.path(Project_folder, 
                      "Concentrator",
                      paste0("Concentrator_quant_",
                             current_sim$quant, 
                             "_alpha_", 
                             current_sim$alpha, 
                             "_sample_", 
                             current_sim$sample) )
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  #active gen id's for that simulation
  active_gen_id <-active_gen_df %>%
    filter(sample == current_sim$sample, quant == current_sim$quant, alpha == current_sim$alpha) %>%
    pull(active_gen_id)
  
  #set active generators
  current_gen <- as_data_frame(exp_IEEE, what = "vertices") %>%
    mutate(Generation_MW = if_else(name %in% active_gen_id, Generation_MW, 0),
           Perc_Gen = Generation_MW/sum(Generation_MW), #find the percentage of total gen for each generator
           Generation_MW = Perc_Gen*sum(Load_MW), #scale generation to match the demand
           Net_Generation = Generation_MW-Load_MW) #reset the net generation column
  
  #set alpha level
  current_g <-as_data_frame(exp_IEEE) %>%
    graph_from_data_frame(., directed = FALSE, vertices = current_gen) %>%
    PowerFlow(., SlackRef_conc, Net_generation = "Net_Generation") %>%
    Proportional_Load(., alpha = 1)
  
  
  #try to speed up simulation by setting not using cascade mode when alpha is Inf
  CascadeMode <- ifelse(is.finite(current_sim$alpha), TRUE, FALSE)
  
  #attack grid
  
  SaveMultiAttacks(current_g, 
                   DeleteOrders_Concentrator_Edges, 
                   folder, 
                   TotalAttackRounds = 1000, 
                   CascadeMode = CascadeMode,
                   Demand = "Load_MW",
                   Generation = "Generation_MW",
                   EdgeName = "Link", 
                   VertexName = "name", 
                   Net_generation = "Net_Generation",
                   Target = "Edges")
  
})
  
```


#extract the data
```{r}


ExtractAttackStats(RootFolder = file.path(Project_folder, "Concentrator"), 
                   NewfolderPath = file.path(Project_folder, "Concentrator_Summary"), 
                   Generation = "Net_Generation",
                   EdgeName = "Link",
                   PowerFlow = "PowerFlow",
                   Link.Limit = "Link.Limit")



#Load the saved files
AttackRoundData <- list.files(path =file.path(Project_folder, "Concentrator_Summary"), 
                              pattern = ".rds", 
                              full.names = TRUE)  %>%
   map_df(~read_rds(.x)) 


test <- AttackRoundData %>%
  arrange(-TotalNodes) %>%
  mutate(has_gc = mean_degree_sqrd > 2*mean_degree) %>%
  filter(!has_gc) %>% 
  group_by(simulationID, alpha) %>%
  summarise_all(first) %>%
  separate(alpha, c("drop1", "drop2","quant","drop3", "alpha_value", "drop4", "sample"), sep = "_") %>%
  mutate(quant = as.integer(quant),
         alpha_value = as.numeric(alpha_value),
         totals = n()) %>%
  select(-contains("drop")) %>%
  group_by(quant, alpha_value) %>%
  summarise_all(mean)

```


#Strain
This looks at how strain functions as a robustness metric

```{r}

Calc_line_strain <- function(g, solved_height_df, distance){
  
  line_strain <-as_data_frame(g) %>% as_tibble %>%
  left_join(., solved_height_df %>% select(node, z), by = c("from"= "node")) %>%
  left_join(., solved_height_df %>% select(node, z), by = c("to"= "node")) %>%
  mutate(dz = abs(z.x-z.y),
         mean_z = (z.x+z.y)/2,
         H = sqrt(dz^2 +{{distance}}^2),
         strain = (H-{{distance}})/{{distance}},
         alpha = Link.Limit/abs(PowerFlow),
         line_load = abs(PowerFlow)/Link.Limit,
         percentile_strain = percent_rank(strain)) %>%
  select(Link, alpha, line_load, dz, H, strain, percentile_strain, mean_z, PowerFlow)
  
}


test <- list.files("/media/jonno/Seagate Expansion Drive/IEEE_Networks/Solved_height_networks", full.names = T) %>%
  map_df(~{
    
    alpha <- basename(.x) %>% gsub("IEEE_118_alpha_", "", .) %>% gsub(".rds", "", .) %>% as.numeric()

    IEEE_118_test<- Proportional_Load(IEEE_118, alpha = alpha) %>%
      set.edge.attribute(. , "distance", value = 1)
    
    read_rds(.x) %>%
      Calc_line_strain(IEEE_118_test , ., distance = distance)

    
  })




test %>%
  ggplot(aes(x = strain, colour = as.factor(alpha))) + geom_density()

test_strain <- test %>%
  mutate(alpha = round(alpha, 5)) %>%
  group_by(alpha) %>%
  summarise(mean = mean(strain),
            median = median(strain),
            weighted.mean = weighted.mean(strain, abs(PowerFlow)),
            counts = n())

test_strain %>%
  ggplot()

test_strain %>%
  gather(key = type, value = strain, -alpha, -counts) %>%
  ggplot(aes(x = 1/alpha, y = strain, colour = type )) + geom_point()

```


#explore convergence

It seems that the algorithm is not converging properly.
I am getting large difference between the infinite model and the a = 10 random ex model.
This below chunk tries to test if 16k and t = 0.3 is good enough, or just what is going on

The algorithm is converging properly. The vairability in the number of nodes needed for complete collapse is so high for low values of alpha that even 100 simualtion has a few dodgy values
```{r}

#calculate theta for all values of alpha
finnesse_prop <-c(1.1, 1.05) %>% map_df(~{
  
  alpha <- .x
  
  print(paste("alpha value", alpha))
  
  current_graph  <- IEEE_118 %>%
    Proportional_Load(., alpha = alpha) %>% 
    set.edge.attribute(. , "distance", value = 1) %>%
    Calc_Spring_Youngs_Modulus(., "PowerFlow", "Link.Limit", 100, 10) %>%
    set.edge.attribute(., "Area", value = 1)
  
  List_of_BiConComps <- Create_balanced_blocks(current_graph, force = "Net_Generation")
  
  #use the largest block to set the simulation parameters k and m.
  #k needs to be sufficiently stretch to allow enough topology variation. otherwise all that happens is a surface angled in the direct of net power flow. Which is interesting but not that interesting
  OriginBlock <- Find_network_balance(List_of_BiConComps[[11]], force = "Net_Generation", 
                                      tstep = 0.01, tol = common_tol, distance = "distance", 
                                      maxIter = 75000, mass = common_mass)
  
  final_z <- Create_stabilised_blocks(current_graph, OriginBlock, 11, force = "Net_Generation", 
                                      tstep = 0.01, tol = common_tol, distance = "distance", 
                                      maxIter = 75000, mass = common_mass) %>%
    mutate(ec = .x)
  
return(final_z)
})


test <-c(1.05, 1.1) %>% map_df(~{
  
test_g <- IEEE_118  %>%
    Proportional_Load(., alpha = .x) %>% 
    set.edge.attribute(. , "distance", value = 1) %>%
    Calc_Spring_Youngs_Modulus(., "PowerFlow", "Link.Limit", 100, 10)
  
  finnesse_prop %>%
    filter(ec == .x) %>%
  Calc_line_strain(test_g, ., distance) 
}) %>%
  mutate(alpha = round(alpha, 5)) %>%
  group_by(alpha) %>%
  summarise(strain = mean(strain))

test2 <- theta_crit_thresh %>%
  mutate(alpha = 1/alpha) %>%
  select(alpha,  NodesAttacked, theta_degs, orig_strain)

```


