---
title: "Untitled"
author: "Jonathan Bourne"
date: "29 April 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

This script is for performing the spring analysis on IEEE_118. The output of this script is used in the Spring Embeddings project. It was kept as a separate script as the outputs my be used more generally in the PhD.

The script requires that the IEEE_118 network has been generated already


This will chunk need to be copy and pasted into the console or the whole RMD file pasted into a new RMD file in AWS.
```{r}
# library("RStudioAMI")
# 
# #Follow instructions to link to dropbox
# linkDropbox()
# 
# #excluding from syncing will probably have to be done a few times, if you have many things in your drop box
# excludeSyncDropbox("*")
# 
# 
# #Once everything is excluded get the key dropbox folders for these simulations
# includeSyncDropbox("IEEE_Networks")
# includeSyncDropbox("Flow_Spring_System")
# includeSyncDropbox("Useful_PhD__R_Functions")
```



```{r}

packages <- c("tidyverse", "igraph", "rlang", "devtools", "minpack.lm" )

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

sapply(packages, library, character.only = TRUE)



install_github("JonnoB/PowerGridNetworking")
library(PowerGridNetworking)

#Set up file system to read the correct folders this switches between aws and windows mode

#This folder is for use on my machine
Project_folder <- "/home/jonno/Dropbox/IEEE_Networks"
#This is for the folder that is on the cloud
#Project_folder <- "~/Dropbox/IEEE_Networks"
IEEE_networks <- file.path(Project_folder, "IEEE_network_files")

#has to point to cloud location if on cloud!
#basewd <- "/home/jonno"
basewd <- "~/Dropbox"

#Load some other useful functions
list.files(file.path(basewd, "Useful_PhD__R_Functions"), pattern = ".R", full.names = T) %>%
  walk(~source(.x))

list.files(file.path(basewd, "Flow_Spring_System"), pattern = ".R", full.names = T) %>%
  walk(~source(.x))

#Load the IEEE-118 network
#This network is created by the markdown script Create_IEEE_NEtworks.Rmd also in this repository
IEEE_118 <- readRDS(file = file.path(IEEE_networks, "IEEE_118_igraph.rds"))
```



#PL attack IEEE118
##Edges
```{r}


setwd(file.path(Project_folder, "IEEE118_edges"))

#rep <-5 #I don't think this does anything. If nothing breaks then delete.
alpha_vector <- c(1, 1.02, 1.01, 1.005, 1.05, 1.1, 1.2, 1.5, 2, 3, 5, 7, 10, 15, 20, 30, 50, 100, 200, Inf)
alpha_vector
set.seed(21256)
DeleteOrders_Edges <- MultiAttackOrder(IEEE_118, Target ="Edges", Sims = 100, Name = "Link")

#Create the simulations for each of the alpha avalues using 100 simulations for each
alpha_vector %>% walk(~{
  gProp <- Proportional_Load(IEEE_118, alpha = .x)

  folder <- paste0("alpha_value_",  .x*100)
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }

  CascadeMode <- ifelse(is.finite(.x), TRUE, FALSE)

  SaveMultiAttacks(gProp, DeleteOrders_Edges, folder,
                   TotalAttackRounds = 1000,
                   CascadeMode = CascadeMode,
                   Demand = "Load_MW",
                   Generation = "Generation_MW",
                   EdgeName = "Link",
                   VertexName = "name",
                   Net_generation = "Net_Generation",
                   Target = "Edges")

}

)



```

##Nodes
I am not doing nodes for this experiment. Previous results (now deleted) suggest that node analysis is not hugely different anyway

#Target orders

Create the target orders for the scrambled edge values
##ec values to attack
```{r}
#The alpha/ec values to scramble
Scramble_ec_values <- c(1.005, 1.01, 1.05, 1.1, 1.2, 1.5, 2, 3, 5, 7, 10, 20) 

#The fraction of edges that will be scrmabled for each scrambled alpha
fract_vect <- c(1, 0.75, 0.5, 0.25) #0.75 can also be added but may overlap with the others too much

```


Generate the target orders that will be used to ensure that the random edge permutations are consistant across the analysis.

This can take a while for large numbers (e.g 10k samples), as each graph needs to be generated and the new alpha value found.
```{r}

target_orders <- fract_vect %>% map_df(~{
  
  file_name <- paste0("target_orders_fract_", .x*100, ".rds")
  
  current_fract <- .x
  
  if(!file.exists(file.path(Project_folder, "target_orders", file_name))){
  
  set.seed(123)
  random_seeds <- sample(1:100000, 10000)
  
  target_orders <- Scramble_ec_values %>% map_df(~{
    
    print(.x)
    #create network
    Scrambled_edge_cap <-  Proportional_Load(IEEE_118, alpha = .x)
    #permute edges
    print("creating the random permutations")
    seed_alpha <- Permute_excess_capacity(Scrambled_edge_cap, random_seeds, fract = current_fract)
    #take subselection
    target_orders <- sub_selection_of_seed_alpha(seed_alpha, total_samples = 10, seed = 123) %>%
      mutate(ec = .x,
             v = 1:n(),
             scramble_fract = current_fract)
    
    return(target_orders)
    
  })
  
  saveRDS(target_orders, file.path(Project_folder, "target_orders", file_name))
  
} else {
  
  target_orders  <- readRDS(file.path(Project_folder, "target_orders", file_name))
  
}
 return(target_orders)
  
})

```

#Fixed EC multi-attack

Two loops

* select fraction
* select scramble value
* attack

The attack goes through all the fractions of scramble as well as all the combinations of random scramble.
It may take a couple of days to calculate. Best done on the cloud if possible

##Edge attack
```{r}

IEEE_118 <- readRDS(file = file.path(IEEE_networks, "IEEE_118_igraph.rds"))

# 
# #These two lines of code are in the PL attack section. the seed ensures the attack order is the same, although it probably doesn't have a very large effect
# set.seed(21256)
# DeleteOrders_Edges <- MultiAttackOrder(IEEE_118, Target ="Edges", Sims = 100, Name = "Link")   
# 
# #fract_vect %>% 
# fract_vect[1] %>%   #used for splitting up the attacks across the fractions
#   walk(~{
#   
#   current_fract <- .x
# 
# Scramble_ec_values %>% 
#   walk(~{
#     
#     target_orders_x <- target_orders %>% 
#       filter(ec == .x, scramble_fract == current_fract)
#     
#     folder <- paste0("alpha_value_",  .x*100) %>%
#       file.path(Project_folder, paste0("IEEE_permute_edge_ec_Edge_fract_", current_fract), .)
#     
#     #create folder if it doesn't already exist
#     if(!file.exists(folder)){
#       dir.create(folder, recursive = TRUE) #create all folders in the path if necessary
#     }
#     
#     #
#     #attack network using the deletion orders
#     #
#     
#     setwd(folder)
#     #create network
#     Scrambled_edge_cap <-  Proportional_Load(IEEE_118, alpha = .x)
#     #attack!
#     Scrambled_Edge_SaveMultiAttacks(target_orders_x, Scrambled_edge_cap, 
#                                     "constant_ec_v", DeleteOrders_Edges, Target = "Edges", fract = current_fract)
#     
#   })
# 
# })

```


#Calculate strain of the selected networks


##Common values
The below chunk was put in due to simulations being run with different parameters resulting in out of synch heights. The common values will be used for both the proportionally loaded edges and the ec scrambled edges
```{r}
common_time <- 0.01
common_Iter <- 20000
common_tol <- 1e-10
common_mass <- 1


Standardisesd_solution_finder <- function(g, common_time, common_Iter, common_tol, common_mass){
  #This function is just a wrapper to tidy up the code chucnks in finding various strain heights for IEEE_118
  
   current_graph  <- g %>%
    set.edge.attribute(. , "distance", value = 1) %>%
    Calc_Spring_Youngs_Modulus(., "PowerFlow", "Link.Limit", minimum_value = 100, stretch_range = 1000) %>%
    set.edge.attribute(., "Area", value = 1) %>%
  Normalize_load(., EdgeName = Link, VertexName = name, Net_Generation = Net_Generation, capacity = Link.Limit)
  

  List_of_BiConComps <- Create_balanced_blocks(current_graph, force = "Net_Generation")

    giant_componant <-List_of_BiConComps %>% map_dbl(~vcount(.x)) %>% which.max()
    
  #use the largest block to set the simulation parameters k and m.
  #k needs to be sufficiently stretch to allow enough topology variation. otherwise all that happens is a surface angled in the direct of net power flow. Which is interesting but not that interesting
      OriginBlock_complete <- Find_network_balance(g = List_of_BiConComps[[giant_componant]], 
                                                   force ="Net_Generation",
                                                   flow = "PowerFlow",
                                                   distance = "distance",
                                                   capacity = "Link.Limit",
                                                   tstep = common_time, 
                                                   tol = common_tol, 
                                                   maxIter = common_Iter, 
                                                   mass = common_mass)
      
      final_z <- Create_stabilised_blocks(g = current_graph, 
                                          OriginBlock = OriginBlock_complete,
                                          OriginBlock_number = giant_componant, 
                                          force ="Net_Generation",
                                          flow = "PowerFlow",
                                          distance = "distance",
                                          capacity = "Link.Limit",
                                          tstep = common_time, 
                                          tol = common_tol, 
                                          maxIter = common_Iter, 
                                          mass = common_mass)
  
  
}

```


##Proportionally loaded spring system

calcualtes the embeddings of the proportionally loaded systems indicated in the alpha vector

```{r}

IEEE_118 <- readRDS(file.path(Project_folder,"IEEE_network_files", "IEEE_118_igraph.rds"))


#Network loadings to find the angles for
alpha_vector <- c(1, 1.02, 1.01, 1.005, 1.05, 1.1, 1.2, 1.5, 2, 2.5, 3, 5, 7, 10, 15, 20, 50, 100, 200, Inf)

if(!file.exists(file.path(Project_folder, "Solved_height_networks_PL"))){
  dir.create(file.path(Project_folder, "Solved_height_networks_PL"))
}


#calculate theta for all values of alpha
alpha_vector %>% walk(~{

  alpha <- .x
  file_path <- file.path(Project_folder,"Solved_height_networks_PL", paste0("IEEE_118_alpha_", alpha, ".rds"))
  
  if(file.exists(file_path)){
    
    print("file exists continueing to next file")
    
  }else {
    
      print(paste("alpha value", alpha))

  current_graph <- IEEE_118 %>% Proportional_Load(., alpha = alpha)

  final_z <- Standardisesd_solution_finder(current_graph, common_time, common_Iter, common_tol, common_mass)

  write_rds(final_z, file_path)
    
  }

})



```


##Scrambled edge embeddings

Calculates the embeddings of the scrambled edge systems across all the fractions

This code is designed to be spread across several machines. It doesn't seem to paralellise well, I am doing something wrong but haven't worked out how to fix it, hence the multiple-machines solution.

An alternative is to assign 1 fraction per machine. Do whatever you want.

```{r}

cpu_id <- 1
number_of_cpus <- 4

target_orders2 <- target_orders %>%
  mutate(file_path = file.path(Project_folder,
                               paste0("constant_ec_from_alpha_fract_", scramble_fract),
                               paste0("Solved_height_networks_alpha_", ec*100),
                               paste0("IEEE_118_alpha_", v, ".rds")),
         calc_on_this_machine = rep_along(file_path, 1:number_of_cpus)) %>%
  filter(calc_on_this_machine == cpu_id,
         ec <= 20)

1:nrow(target_orders2) %>%
  walk(~{
    
    target <- target_orders2 %>%
      slice(.x)
    
    #does the file exist?
    if(file.exists(target$file_path)){
      print("file exists continueing to next file")
    }else { 
      
      #if the file doesn't exist ensure that the folder is created and then calculate
      if(!dir.exists(dirname(target$file_path))){
        dir.create(dirname(target$file_path), recursive = TRUE)
      }
      
      print(paste0("fraction ", target$scramble_fract ," ec value ", target$ec, ". v ",target$v))
      #create network
      Scrambled_edge_cap <-  Proportional_Load(IEEE_118, alpha = target$ec)
      
      #create dataframe of new edge limits
      temp <-Create_scrambled_edges(Scrambled_edge_cap, target$seed, fract = target$scramble_fract)
      
      print(mean(temp$alpha))
      
      final_z <- Standardisesd_solution_finder(Scrambled_edge_cap %>%
                                                 set.edge.attribute(., "Link.Limit", value = temp$Link.Limit), 
                                               common_time, common_Iter, common_tol, common_mass)
      
      write_rds(final_z, target$file_path)
      
    } #proceed to next iteration
    
  })

```



#Dummy Chunk
run all the chunks above
```{r}

```


#Strain and quantity

I beleive that strains link to robustness is mediated throught the concentration of demand and generation nodes.
I will test this by doing the following on the largest block of the IEEE 118 network
Using the largest component prevents dead areas of the network and ensures that the all the experiments are topologically identical

5 quantities of generator fraction is used either 17, 12, 8, 4, 1, or a single generator 
20 random samples of each generator level
5 alpha levels 1, 1.5, 2, 5, Inf

This makes 500 different combinations to try + 5 at 100% of all generators

I then 

```{r}

IEEE_118 <- readRDS(file = file.path(IEEE_networks, "IEEE_118_igraph.rds"))

#alpha levels of the concentrator
alpha_conc <- c(1, 1.5, 2, 5, Inf)

List_of_BiConComps <- Create_balanced_blocks(IEEE_118, force = "Net_Generation")

giant_componant <-List_of_BiConComps %>% map_dbl(~vcount(.x)) %>% which.max()

exp_IEEE <- List_of_BiConComps[[giant_componant]]

#In this case the base slack ref will be the largest power consumer
SlackRef_conc <- "59"

#Generate Attack orders
set.seed(21256)
DeleteOrders_Concentrator_Edges <- MultiAttackOrder(exp_IEEE, Target ="Edges", Sims = 100, Name = "Link")  


#get the node id of all the generators
gen_id <- as_data_frame(exp_IEEE, what = "vertices") %>% filter(Generation_MW >0) %>% pull(name) 

#make a df of all combinations of sample size and sample iteration
combs <- expand.grid(x = c(4,8,12), y = 1:20) %>%
  as_tibble 

quant_alpha_comb <- expand.grid(quant = c(17, 12, 8, 4, 1), alpha = alpha_conc) %>%
  as_tibble


active_gen_df <- map2_df(.x  = combs$x, .y = combs$y, ~{
  
  tibble(active_gen_id =  sample(gen_id, .x, replace = FALSE), sample = .y, quant = .x)
  
}) %>%
  bind_rows(tibble(active_gen_id =  gen_id, sample = 1, quant = 17)) %>% #there is only 1 combination of all generators
  bind_rows(tibble(active_gen_id =  gen_id, sample = 1:17, quant = 1)) %>% #there are only 17 for sample size of 1 so this is added on after the others
left_join(quant_alpha_comb,., by = "quant" ) #join so that each specific quant-sample combo is represented at each alpha quant

#the unique simulation combos to be calculated
simulation <-active_gen_df %>% 
  select(-active_gen_id) %>%
  distinct()

cpu_id <- 4
number_of_cpus <- 4
cpu_vector <- rep(1:number_of_cpus, length.out = nrow(simulation))
cpu_sims <-(1:nrow(simulation))[cpu_vector==cpu_id]


cpu_sims %>% walk(~{
  #set the simulation to calculate
  current_sim <- simulation %>%
    slice(.x)
  
  #folder name is 
  folder <- file.path(Project_folder, 
                      "Concentrator",
                      paste0("Concentrator_quant_",
                             current_sim$quant, 
                             "_alpha_", 
                             current_sim$alpha, 
                             "_sample_", 
                             current_sim$sample) )
  #create folder if it doesn't already exist
  if(!file.exists(folder)){
    dir.create(folder)
  }
  
  #active gen id's for that simulation
  active_gen_id <-active_gen_df %>%
    filter(sample == current_sim$sample, quant == current_sim$quant, alpha == current_sim$alpha) %>%
    pull(active_gen_id)
  
  #set active generators
  current_gen <- as_data_frame(exp_IEEE, what = "vertices") %>%
    mutate(Generation_MW = if_else(name %in% active_gen_id, Generation_MW, 0),
           Perc_Gen = Generation_MW/sum(Generation_MW), #find the percentage of total gen for each generator
           Generation_MW = Perc_Gen*sum(Load_MW), #scale generation to match the demand
           Net_Generation = Generation_MW-Load_MW) #reset the net generation column
  
  #set alpha level
  current_g <-as_data_frame(exp_IEEE) %>%
    graph_from_data_frame(., directed = FALSE, vertices = current_gen) %>%
    PowerFlow(., SlackRef_conc, Net_generation = "Net_Generation") %>%
    Proportional_Load(., alpha = 1)
  
  
  #try to speed up simulation by setting not using cascade mode when alpha is Inf
  CascadeMode <- ifelse(is.finite(current_sim$alpha), TRUE, FALSE)
  
  #attack grid
  
  SaveMultiAttacks(current_g, 
                   DeleteOrders_Concentrator_Edges, 
                   folder, 
                   TotalAttackRounds = 1000, 
                   CascadeMode = CascadeMode,
                   Demand = "Load_MW",
                   Generation = "Generation_MW",
                   EdgeName = "Link", 
                   VertexName = "name", 
                   Net_generation = "Net_Generation",
                   Target = "Edges")
  
})
  
```


#extract the data
```{r}


ExtractAttackStats(RootFolder = file.path(Project_folder, "Concentrator"), 
                   NewfolderPath = file.path(Project_folder, "Concentrator_Summary"), 
                   Generation = "Net_Generation",
                   EdgeName = "Link",
                   PowerFlow = "PowerFlow",
                   Link.Limit = "Link.Limit")



#Load the saved files
AttackRoundData <- list.files(path =file.path(Project_folder, "Concentrator_Summary"), 
                              pattern = ".rds", 
                              full.names = TRUE)  %>%
   map_df(~read_rds(.x)) 


test <- AttackRoundData %>%
  arrange(-TotalNodes) %>%
  mutate(has_gc = mean_degree_sqrd > 2*mean_degree) %>%
  filter(!has_gc) %>% 
  group_by(simulationID, alpha) %>%
  summarise_all(first) %>%
  separate(alpha, c("drop1", "drop2","quant","drop3", "alpha_value", "drop4", "sample"), sep = "_") %>%
  mutate(quant = as.integer(quant),
         alpha_value = as.numeric(alpha_value),
         totals = n()) %>%
  select(-contains("drop")) %>%
  group_by(quant, alpha_value) %>%
  summarise_all(mean)

```


#Strain
This looks at how strain functions as a robustness metric

```{r}

Calc_line_strain <- function(g, solved_height_df, distance){
  
  line_strain <-as_data_frame(g) %>% as_tibble %>%
  left_join(., solved_height_df %>% select(node, z), by = c("from"= "node")) %>%
  left_join(., solved_height_df %>% select(node, z), by = c("to"= "node")) %>%
  mutate(dz = abs(z.x-z.y),
         mean_z = (z.x+z.y)/2,
         H = sqrt(dz^2 +{{distance}}^2),
         strain = (H-{{distance}})/{{distance}},
         alpha = Link.Limit/abs(PowerFlow),
         line_load = abs(PowerFlow)/Link.Limit,
         percentile_strain = percent_rank(strain)) %>%
  select(Link, alpha, line_load, dz, H, strain, percentile_strain, mean_z, PowerFlow)
  
}


test <- list.files("/media/jonno/Seagate Expansion Drive/IEEE_Networks/Solved_height_networks", full.names = T) %>%
  map_df(~{
    
    alpha <- basename(.x) %>% gsub("IEEE_118_alpha_", "", .) %>% gsub(".rds", "", .) %>% as.numeric()

    IEEE_118_test<- Proportional_Load(IEEE_118, alpha = alpha) %>%
      set.edge.attribute(. , "distance", value = 1)
    
    read_rds(.x) %>%
      Calc_line_strain(IEEE_118_test , ., distance = distance)

    
  })




test %>%
  ggplot(aes(x = strain, colour = as.factor(alpha))) + geom_density()

test_strain <- test %>%
  mutate(alpha = round(alpha, 5)) %>%
  group_by(alpha) %>%
  summarise(mean = mean(strain),
            median = median(strain),
            weighted.mean = weighted.mean(strain, abs(PowerFlow)),
            counts = n())

test_strain %>%
  ggplot()

test_strain %>%
  gather(key = type, value = strain, -alpha, -counts) %>%
  ggplot(aes(x = 1/alpha, y = strain, colour = type )) + geom_point()

```


#explore convergence

It seems that the algorithm is not converging properly.
I am getting large difference between the infinite model and the a = 10 random ex model.
This below chunk tries to test if 16k and t = 0.3 is good enough, or just what is going on

The algorithm is converging properly. The vairability in the number of nodes needed for complete collapse is so high for low values of alpha that even 100 simualtion has a few dodgy values
```{r}

#calculate theta for all values of alpha
finnesse_prop <-c(1.1, 1.05) %>% map_df(~{
  
  alpha <- .x
  
  print(paste("alpha value", alpha))
  
  current_graph  <- IEEE_118 %>%
    Proportional_Load(., alpha = alpha) %>% 
    set.edge.attribute(. , "distance", value = 1) %>%
    Calc_Spring_Youngs_Modulus(., "PowerFlow", "Link.Limit", 100, 10) %>%
    set.edge.attribute(., "Area", value = 1)
  
  List_of_BiConComps <- Create_balanced_blocks(current_graph, force = "Net_Generation")
  
  #use the largest block to set the simulation parameters k and m.
  #k needs to be sufficiently stretch to allow enough topology variation. otherwise all that happens is a surface angled in the direct of net power flow. Which is interesting but not that interesting
  OriginBlock <- Find_network_balance(List_of_BiConComps[[11]], force = "Net_Generation", 
                                      tstep = 0.01, tol = common_tol, distance = "distance", 
                                      maxIter = 75000, mass = common_mass)
  
  final_z <- Create_stabilised_blocks(current_graph, OriginBlock, 11, force = "Net_Generation", 
                                      tstep = 0.01, tol = common_tol, distance = "distance", 
                                      maxIter = 75000, mass = common_mass) %>%
    mutate(ec = .x)
  
return(final_z)
})


test <-c(1.05, 1.1) %>% map_df(~{
  
test_g <- IEEE_118  %>%
    Proportional_Load(., alpha = .x) %>% 
    set.edge.attribute(. , "distance", value = 1) %>%
    Calc_Spring_Youngs_Modulus(., "PowerFlow", "Link.Limit", 100, 10)
  
  finnesse_prop %>%
    filter(ec == .x) %>%
  Calc_line_strain(test_g, ., distance) 
}) %>%
  mutate(alpha = round(alpha, 5)) %>%
  group_by(alpha) %>%
  summarise(strain = mean(strain))

test2 <- theta_crit_thresh %>%
  mutate(alpha = 1/alpha) %>%
  select(alpha,  NodesAttacked, theta_degs, orig_strain)

```


