---
title: "Untitled"
author: "Jonathan Bourne"
date: "7 January 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

This code explores the effect of what is removed on the amount of overloads/islands/targeted on the system

#Setup Block

```{r}

packages <- c("tidyverse", "igraph","readr","readxl", "broom", "zoo", "stringr","foreach", "doMC",  "xtable", "geomnet", "ggnetwork", "rlang", "animation", "ggridges", "poweRlaw", "Rtsne", "caret", "ranger", "xtable", "broom", "modelr", "yardstick", "sf", "rgdal", "foreach", "doMC")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)


sapply(packages, library, character.only = TRUE)


lapply(packages, library, character.only = TRUE)
library(PowerGridNetworking)

select <- dplyr::select

#Set up file system to read the correct folders this switches between aws and windows mode

basewd <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder"
datafile <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder/ETYSAppendixB"
#LatexFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Proportional Line Limits" 
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")
#Functions <-"/home/jonno/Create_ETYS_network/Functions"
Tariff <- file.path(basewd,"Tariff and Transport")
PLwd <- "/media/jonno/Seagate Expansion Drive/Innoculation"
Saved_Sims <- file.path(PLwd, "Saved_Sims")
Deletion_Order_Folder <-  file.path(PLwd, "DeletionOrder") #Only one of the deletion order folders is needed. Either Nodes or Edges
Deletion_Order_Folder <- file.path(PLwd, "DeletionOrder_Nodes")
StratAttackWd <- "/media/jonno/Seagate Expansion Drive/ProportionalLoading/StratAttack"

source("/home/jonno/Create_ETYS_network/SubCode/LoadData2.R")


#FOr NetSci
#FiguresFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/NetSci2018 Poster/Figures"
```

#Create the Attack Orders
```{r}
#Set the path to a large enough storage
setwd(PLwd)

#Ensure there is powerflow
g <- PowerFlow(gbase, "FECK40")

g %>%
  simplify(., remove.multiple = T, remove.loops = T) %>% 
    plot(.,vertex.size=.8, edge.arrow.size=.4, vertex.label=NA)

NetworkStats(g) %>%
  xtable() %>% print(type = "latex", file = file.path(FiguresFolder, "NetworkStats.txt"))

AttackRounds <- 1000

#Create a reproducible attack order
seed<- 1589
filename <- "DeleteOrders100.rds"
if(file.exists(filename)){
  DeleteOrders <- readRDS(filename)
} else {
set.seed(seed)
DeleteOrders <- MultiAttackOrder(gbase, 100)  
saveRDS(DeleteOrders, filename)
}

```

#Set alpha colour gradient
```{r}
  AlphaGrad <-scale_colour_gradientn(colors = c("red",   "limegreen"),
                          breaks = c(1,2,7,20,50),
                          trans = "log",
                          values = scales::rescale((c(0, 6, 7, 20, 50))),
                          name = expression(alpha*" level")) #"Alpha value"
```




#remove keep Load/gen from targets

```{r}
#This includes trans1 but doesn't mention that.
#It needs to be explicitly used in the function or betterstill replaced with g
SelectiveDelete <- function(DeleteOrders, filterCond){

  TransferNodes <- 1:nrow(DeleteOrders) %>% map_df(~{

  test <- DeleteOrders[.x,-1] %>% 
  gather(key = Target, value = Node) %>%
  left_join(., trans1 %>% select(Node = Bus.Name, NetGen = BusTransferB), by = "Node") %>%#smaller than 0 is demand larger is gen
  filter(!!filterCond) %>%
  select(-NetGen) %>%
    mutate(Target = 1:n()) %>% #Renumber the nodes so there are no NA values where certain nodes have been removed
  spread(key = Target, value = Node) %>%
    set_names(paste0("Target_", names(.))) #Add back in the word "Target"
  
}) %>%
  mutate(SimulationID = paste0("Simulation_ID_", 1:nrow(DeleteOrders))) %>%
    select(SimulationID, everything() )
  
  
}


TransferNodes <- SelectiveDelete(DeleteOrders, filterCond = quo(NetGen == 0))
GenNodes <- SelectiveDelete(DeleteOrders, filterCond = quo(NetGen > 0))
LoadNodes <- SelectiveDelete(DeleteOrders, filterCond = quo(NetGen < 0))
NonTransferNodes <- SelectiveDelete(DeleteOrders, filterCond = quo(NetGen != 0))
GenTransferNodes <- SelectiveDelete(DeleteOrders, filterCond = quo(NetGen >= 0))
LoadTransferNodes <- SelectiveDelete(DeleteOrders, filterCond = quo(NetGen <= 0))
```


```{r}

list("TransferNodes", "GenNodes", "LoadNodes", "NonTransferNodes", "GenTransferNodes", "LoadTransferNodes") %>%
  walk(~{
    
  setwd(Saved_Sims)

  folder <-.x
  print(folder)

    if(!file.exists(folder)){
      dir.create(folder)
    }

  DeleteOrders <- get(.x)
#   
#   n <- 6
# 
# groups <- split(1:nrow(DeleteOrders), sort(rep_len(1:n, length(1:nrow(DeleteOrders)))))
# 
# registerDoMC(n)
# foreach (i = 1:n) %dopar% {
# 
#  SaveMultiAttacks(g, DeleteOrders[groups[[i]],], folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
#   
# }

  
  SaveMultiAttacks(g, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)

   
  })






```


Get the round number that an edge was deleted.

```{r}

FolderVect <- list.files(path = Saved_Sims) #folder where all the alpha FOLDERS are
FileVect <- list.files(path = Deletion_Order_Folder) %>% gsub(".rds", "",.) #folder where all the deletion order FILES are
new.type <- FolderVect[!(FolderVect %in% FileVect)] #The FOLDERS that are not present as FILES

if(length(new.type)>0){
file.path(Saved_Sims, new.type) %>%
  walk( ~{
    print(.x) #print name of folder where deletion order will be calculated
    
  Removeddf <- list.files(path = .x, full.names = TRUE) %>% #list the different network of network rds files present
    map_df(~{
        file <- .x
        print(file)
        read_rds(file) %>%
          RoundTypeRemoved (.)  %>%
          mutate(Sim = gsub(".rds", "",file) %>% basename)
      }
    ) %>%
    group_by(Sim) %>%
    mutate(RoundRemoved = ifelse(is.na(RoundRemoved), max(RoundRemoved), RoundRemoved),
         alpha = basename(.x)) %>% 
    ungroup

  Removeddf %>%
        write_rds(x = ., paste0(file.path(Deletion_Order_Folder,basename(.x)), ".rds"))
  }
  )

} 
  
AllRemovedNodes <- list.files(Deletion_Order_Folder, full.names = TRUE) %>%
  map_df(~read_rds(.x))


CleanNames <- function(df, TargetColumn, AlphaOrder){
temp <- df  %>%
  mutate_(temp1 = TargetColumn) %>%
 mutate(temp2 = temp1,
          temp2 = temp1 %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9])+")%>% as.numeric(.)/100,
temp3 = temp1 %>%
  str_replace_all(., "_", " ") %>%
  str_extract_all(., "([aA-zZ\\s])+", T) %>%
  paste0(., ifelse(is.na(temp2), "", temp2)),
        temp3 = temp3 %>% as.factor() %>%
  fct_relevel(., AlphaOrder)
) %>%
  select(temp3)
temp <-temp  %>% set_names(paste0(TargetColumn,"2")) 
 
temp <- bind_cols(df, temp)
return(temp)
}


```

```{r}
 LossFractionByRound <- AllRemovedNodes %>%
  group_by(Sim, alpha, type, RoundRemoved, RemovalType) %>%
  summarise(counts = n()) %>%
  group_by(Sim, alpha, type, RemovalType) %>%
  mutate(cumsum = cumsum(counts)) %>%
  group_by(alpha, type, RoundRemoved, RemovalType) %>%
  summarise(mean = mean(counts),
            median = median(counts),
            sd = sd(counts),
            cummean = mean(cumsum),
            cummedian = median(cumsum),
            cumsd = sd(cumsum)) %>%
  left_join(tibble(type = c("Edge", "Node"), 
                    tot = c(ecount(gbase), vcount(gbase)))
            ) %>%
  group_by(alpha, type, RemovalType) %>%
  mutate( test = cumsum(median),
          testfrac = test/tot,
    cummeanfrac = cummean/tot,
            cummedianfrac = cummedian/tot)



#This plot shows that randonly attacking all nodes is LESS effective than targeting a subset of nodes in terms of islanding.
#However there is basically no overloading when targeting the subsets
LossFractionByRound %>%
  filter(RoundRemoved<100) %>% #Keep everything on rought the same scale
  filter(type == "Node", RemovalType != "Targeted") %>%
  ggplot(aes(x = RoundRemoved, y = cummean, group = alpha, colour = alpha)) + geom_line() + 
  facet_wrap(~RemovalType, scales = "free_y")
  


Loss2 <- AllRemovedNodes %>%
  group_by(Sim, alpha, type, RoundRemoved, RemovalType) %>%
  summarise(counts = n()) %>%
  group_by(Sim, alpha, type, RemovalType) %>%
  mutate(cumsum = cumsum(counts)) 


Loss2 %>%
  filter(type == "Node", RemovalType == "Islanded") %>%
  ggplot(aes(x = RoundRemoved, y = cumsum, group = Sim, colour = alpha)) + geom_line() + 
  facet_wrap(.~alpha) +
  coord_cartesian(xlim = c(0,100), ylim = c(0,300))


Loss3 <- Loss2 %>%
  group_by(Sim, type, alpha, RemovalType) %>%
  summarise(cumsum = max(cumsum)) %>%
  spread(key = RemovalType, value = cumsum)

#Strong negative corellation with between Targeted and overload for edge removal, but also for Islanded... What?
Loss3 %>%
  filter(type == "Node", alpha != "AllNodes") %>%
  ggplot(aes(x = Islanded, y = Targeted)) +
  geom_point()+ 
  facet_wrap(.~alpha)

   Loss3 %>%
 # filter(type == "Node", alpha == "Real_Limits") %>%
     group_by(alpha, type) %>%
     summarise(corTargOver = cor(Targeted, Overloaded, use =  "pairwise.complete.obs"),
               corTargIsl = cor(Targeted, Islanded, use =  "pairwise.complete.obs"),
               corOverIsl = cor(Overloaded, Islanded, use =  "pairwise.complete.obs")) %>%
     arrange(type)
   
   

   #There Only the full random attack has overloads   
 AllRemovedNodes %>%
     filter(RoundRemoved<100) %>% #Keep everything on rought the same scale
  group_by(type, alpha, Sim, RemovalType) %>%
  summarise(counts = n()) %>%
 #bind_rows(., NumberofRounds) %>%
     filter(type == "Node") %>%
   ggplot(aes(x = alpha, y = counts)) + geom_boxplot() + 
   facet_wrap(type~RemovalType, scales = "free_y") +
    theme(legend.position = "none", 
        axis.text.x = element_text(angle = 45, hjust = 1)) 


```




#Make a really large number of random attacks

```{r}
AttackRounds<- 1000

#Create a reproducible attack order
seed<- 1589
filename <- "DeleteOrders10k.rds"
if(file.exists(filename)){
  DeleteOrders <- readRDS(filename)
} else {
set.seed(seed)
DeleteOrders <- MultiAttackOrder(gbase, 10000)  
saveRDS(DeleteOrders, file.path(PLwd, filename))
}

```



```{r}
folder <- "Random_Attacks"

  if(!file.exists(folder)){
    dir.create(folder)
  }

SaveMultiAttacks(g, DeleteOrders, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
```


##Multicore attacks

This doesn't work but I don't understand why

```{r}
library(foreach)
library(doMC)

folder <- "Random_Attacks"

  if(!file.exists(folder)){
    dir.create(folder)
  }


n <- 4

groups <- split(1:nrow(DeleteOrders), sort(rep_len(1:n, length(1:nrow(DeleteOrders)))))

registerDoMC(n)
foreach (i = 1:n) %dopar% {

 SaveMultiAttacks(g, DeleteOrders[groups[[i]],], folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
  
}
```





#Scramble node function
```{r}



```



```{r}

seed<- 1589
filename <- "DeleteOrders100.rds"
if(file.exists(filename)){
  DeleteOrders <- readRDS(filename)
} else {
set.seed(seed)
DeleteOrders <- MultiAttackOrder(gbase, 100)  
saveRDS(DeleteOrders, filename)
}

#Make simulations order
NewFunctionOrder <- NodeCharacteristiceScrambler(gbase, 100)
  
```

##Generate Stategies
```{r}




```

#Simaulate attacks using strategies
```{r}
setwd(file.path(PLwd, "Scramble", "Strategy"))

for(n in 1:(ncol(NewFunctionOrder)-1)){
 
 Sim_Order<- NewFunctionOrder  %>% select(-1) %>% pull(n)
  
  g <- ReOrderGraph(gbase, Sim_Order)
  #calculate Flow
  g <- PowerFlow(g, "FECK40")
  #Make edges proportional to flow
  g<- Proportional_Load(g, alpha = 5)
  
  folder <- paste0("Order_", n)
  
    if(!file.exists(folder)){
      dir.create(folder)
    }
  
  StratAttackVect <- CreateStrategyAttackDf(g)

SaveMultiAttacks(g,  StratAttackVect, folder, TotalAttackRounds = AttackRounds, CascadeMode = T)
}

```

#Extract data for scrambles


```{r}
ExtractAttackStats("/media/jonno/Seagate Expansion Drive/Innoculation/Scramble/Strategy", file.path(PLwd, "Attack_Strategy_SummaryData"))


AttackRoundData <- list.files(path = file.path("/media/jonno/Seagate Expansion Drive/ProportionalLoading","SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x)) %>%
  filter(alpha == "alpha_value_500") %>%
  mutate(Strategy = "RandomAttack",
  PercNum = NodesAttacked/958) %>% 
  group_by(NodesAttacked) %>%
  mutate(rankblack = min_rank(-Blackout),
         rankGC = min_rank(GCfract)) %>%
  ungroup %>%
  SummariseMonteCarlo %>%
  mutate(PercNum = NodesAttacked/958)


AttackStratRoundData <- list.files(path = file.path(PLwd,"Attack_Strategy_SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x)) %>%
  mutate(Strategy = case_when(
    simulationID == "1" ~"Degree" ,
    simulationID == "2" ~"EntDeg_LinkLimit",
    simulationID == "3" ~"EntDeg_PowerFlow",
    simulationID == "4" ~"Elec_Centrality",
    TRUE ~ "Centrality"
  ),
  simulationID = alpha %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9])+")%>% as.numeric(.),
  PercNum = NodesAttacked/958) %>% 
  group_by(NodesAttacked, alpha) %>%
  mutate(rankblack = min_rank(-Blackout),
         rankGC = min_rank(GCfract)) %>%
  ungroup


SummaryofGC<- AttackStratRoundData %>%
  SummariseMonteCarlo %>%
  mutate(PercNum = NodesAttacked/958) %>%
  bind_rows(AttackRoundData)

 NodeCollapse <- rbind(SummaryofGC %>%
  select(PercNum, mean, Strategy, GC05, GC95, sd, NodesAttacked) %>% mutate(type = "Giant componant size reduction"),
SummaryofGC %>% 
  select(PercNum, mPGfract, Strategy, PG05, PG95, sdPGfract, NodesAttacked) %>% 
  mutate(type = "Blackout size") %>%
  rename(mean = mPGfract, GC05 = PG05, GC95 = PG95, sd = sdPGfract)
) %>% mutate(Target = "Node") 

test <- NodeCollapse %>% #need to remove infinte values 
    filter(is.finite(mean), PercNum < 0.5)  


#This shows that the strategy attack on random orders is more aggressive than the random attack on the true order but not much more than that
 test %>% 
  filter(Strategy != "RandomAttack")  %>%
  ggplot(aes(x = PercNum, y =  mean, group = Strategy)) + 
  geom_line(aes(colour = Strategy), show.legend = TRUE) +
  geom_line(data =  test %>% 
  filter(Strategy == "RandomAttack") , aes(colour = 'Real'), color = 'black', linetype ="longdash") +
    facet_grid(~type)

```

#Plot the mean difference between strategies with random nodes and the true order
```{r}


AttackStratRoundData2 <- list.files(path = file.path("/media/jonno/Seagate Expansion Drive/ProportionalLoading","Attack_Strategy_SummaryData"), 
                              pattern = ".rds", 
                              full.names = TRUE) %>%
   map_df(~read_rds(.x)) %>%
  mutate(simulationID = case_when(
    simulationID == "1" ~"Degree" ,
    simulationID == "2" ~"EntDeg_LinkLimit",
    simulationID == "3" ~"EntDeg_PowerFlow",
    simulationID == "4" ~"Elec_Centrality",
    TRUE ~ "Centrality"
  ),
  alpha1 = alpha %>%
           str_replace_all(., "_", " ") %>%
           str_extract_all(., "([0-9])+")%>% as.numeric(.)/100,
alpha = alpha %>%
  str_replace_all(., "_", " ") %>%
  str_extract_all(., "([aA-zZ\\s])+", T) %>%
  paste0(., ifelse(is.na(alpha1), "", alpha1)),
  alpha = fct_relevel(alpha, "alpha value 5", after=2) %>%
  fct_relevel(., "alpha value 2", after=2) %>%
  fct_relevel(., "alpha value 1.5", after=2),
  PercNum = NodesAttacked/958) %>% 
  group_by(NodesAttacked, alpha) %>%
  mutate(rankblack = min_rank(-Blackout),
         rankGC = min_rank(GCfract)) %>%
  ungroup %>%
  filter(alpha == "alpha value 5") %>%
  mutate(Strategy = simulationID, 
         simulationID = 1)



test <- NodeCollapse %>%
  filter(type != "Giant componant size reduction") %>%
  left_join(AttackStratRoundData2) %>%
  mutate(meanDiff = mean -Blackout,
         meanRatio = mean/Blackout)

test %>%
  filter(!is.na(MaxComp)) %>%
   ggplot(aes(x = PercNum, y =  meanDiff, group = Strategy)) + 
  geom_line(aes(colour = Strategy), show.legend = TRUE) +#
  labs(title = "Mean difference from the True node function")

#
test %>%
  filter(Strategy != "RandomAttack") %>%
  select(PercNum, mean, Strategy, Blackout) %>%
  gather(key = "type", value = "value", -Strategy, -PercNum) %>%
  ggplot(aes(x = PercNum, y = value, colour = type)) + 
  geom_line() + 
  facet_wrap(~Strategy)


test <- AttackStratRoundData %>%
  mutate(type = "Scramble") %>%
  bind_rows(., AttackStratRoundData2 %>% mutate(type = "Original",
                                               simulationID = 1e6)) 

#A lot of simulations go through a rapid network collapse after having a relatively linear period of growth
test %>%
#  select(PercNum, mean, Strategy, Blackout) %>%
  ggplot(aes(x = PercNum, y = Blackout, colour = type, group = simulationID)) + 
  geom_line() +
  facet_wrap(~Strategy)+
  labs(x = "Percentage of nodes Attacked", title = "Comparing scrambled networks with the real network using different strategies")

#A density plot of the end point shows that there is a tendency to to collapse early
test2 <- test %>%
  group_by(simulationID, Strategy) %>%
  summarise(NodesAttacked = max(NodesAttacked),
            PercNum = max(PercNum))
test2 %>%
  ggplot(aes(x = NodesAttacked, colour = Strategy)) + geom_density()
  

test2 <- AttackStratRoundData %>%
  left_join(., AttackStratRoundData2 %>% select(NodesAttacked, Strategy,  BlackoutTRUE = Blackout, GCTRUE = GCfract), by = c("NodesAttacked", "Strategy"))

SimEval <- expand.grid(unique(test2$Strategy), unique(test2$simulationID)) %>%
  map2_df(.x = .$Var1, .y = .$Var2, .f = ~{
    
  Temp <-  test2 %>%
  filter(Strategy== .x, simulationID==.y) %>%
    select(Blackout, BlackoutTRUE) %>% 
    filter(complete.cases(.))
  metrics(Temp, truth = BlackoutTRUE, estimate = Blackout) %>% 
    select(metric = .metric, estimate = .estimate) %>%
  #  spread(key = metric, value = estimate) %>%
    mutate(Strategy = .x, SimulationID = .y)
    
  })


#There is substantial difference between the strategies
SimEval %>%
  filter(metric != "mae") %>%
  ggplot(aes(x = Strategy, y = estimate, fill = Strategy)) + geom_boxplot()+
    facet_wrap(metric~., ncol = 1, scales = "free_y") +
  theme(legend.position="none")

```


#Extract Scramble graph vulnerability metrics

```{r}
NewFunctionOrder <- NodeCharacteristiceScrambler(gbase, 100)

StratScrambleVuln <- 1:100 %>% map_df(~{
 
  print(.x)
 Sim_Order<- NewFunctionOrder  %>% select(-1) %>% pull(.x)
  
  g <- ReOrderGraph(gbase, Sim_Order)
  #calculate Flow
  g <- PowerFlow(g, "FECK40")
  #Make edges proportional to flow
  g <- Proportional_Load(g, alpha = 5)

  tibble(
    Order = .x,
    name = get.vertex.attribute(g, "name"),
    #Elec_Centrality = ElectricalCentrality(g)$NodeEC,
       Degree = degree(g),
       Centrality  = betweenness(g, normalized = TRUE),
       EntDeg_LinkLimit = EntropicDegree(g, Scale = TRUE),
       EntDeg_PowerFlow = EntropicDegree(g, value = "PowerFlow", Scale = TRUE),
    Generator = get.vertex.attribute(g, "Generation")>0 | get.vertex.attribute(gstandard, "Demand")<0,
    Demand = get.vertex.attribute(g, "Demand")>0
       ) %>%
    left_join(.,  ElectricalCentrality(g)$NodeEC %>% 
                rename(Elec_Centrality = NodeEC, name = Bus.Name))

}) %>% mutate( Transfer = !(Generator |Demand),
       NodeType = case_when(
         Transfer ~ 1, #If transfer is true the node type is transfer
         Demand ~ 2, #if case a is flase but Demand is TRUE then the type is DEmand
         TRUE ~ 3
       ))


saveRDS(StratScrambleVuln, file.path(PLwd, "StratScrambleVuln.rds"))
#readRDS(file.path(PLwd, "StratScrambleVuln.rds"))

test <- StratScrambleVuln %>%
 select(GroupVar = Demand, Degree:EntDeg_PowerFlow, Elec_Centrality)

test %>%
  ggplot(aes(x = GroupVar, y = Elec_Centrality)) + geom_boxplot()

2:ncol(test) %>% map_df(~{
  
  Temp <- test %>%
  select(GroupVar, target = .x) %>%
  filter(is.finite(target))
  
  
  Temp %>%
  group_by(GroupVar) %>%
  summarise(counts = n(),
            mean = mean(target),
            median = median(target),
            sd = sd(target)) %>%
    mutate(
      SignifDiff = t.test(Temp$target[Temp$GroupVar], Temp$target[!Temp$GroupVar])$p.value<0.05,
      type = names(test)[.x])
})


test2 <- t.test(Temp$target[Temp$GroupVar], Temp$target[!Temp$GroupVar])

 gstandard <- PowerFlow(gbase, "FECK40")

 StandardVuln <- tibble(
    Order = 1e5,
    name = get.vertex.attribute(gstandard, "name"),
    #Elec_Centrality = ElectricalCentrality(gstandard)$NodeEC,
       Degree = degree(gstandard),
       Centrality  = betweenness(gstandard, normalized = TRUE),
       EntDeg_LinkLimit = EntropicDegree(gstandard, Scale = TRUE),
       EntDeg_PowerFlow = EntropicDegree(gstandard, value = "PowerFlow", Scale = TRUE),
    Generator = get.vertex.attribute(gstandard, "Generation")>0 | get.vertex.attribute(gstandard, "Demand")<0,
    Demand = get.vertex.attribute(gstandard, "Demand")>0,
    Transfer = !(Generator |Demand),
       NodeType = case_when(
         Transfer ~ 1, #If transfer is true the node type is transfer
         Demand ~ 2, #if case a is flase but Demand is TRUE then the type is DEmand
         TRUE ~ 3
       )) %>%
    left_join(.,  ElectricalCentrality(gstandard)$NodeEC %>% 
                rename(Elec_Centrality = NodeEC, name = Bus.Name))
 
 
test <- StandardVuln %>% mutate(Real = 1) %>%
  bind_rows(StratScrambleVuln%>% mutate(Real = 0)) %>%
  mutate_all(function(Var){ifelse(is.finite(Var), Var, 0)}) %>%
 select(NodeType, Degree:EntDeg_PowerFlow, Elec_Centrality, Real) %>%
  gather(key = "Metric", value = "value", -NodeType, -Real) %>%
  mutate( NodeType = case_when(
        NodeType== 1 ~ "Transfer", #If transfer is true the node type is transfer
        NodeType== 2 ~"Demand", #if case a is flase but Demand is TRUE then the type is DEmand
         TRUE ~ "Generator"
       ))


#How the real and synthetic nodes vary
#why is there any difference between synth nodetypes? shouldn't they all be the same?
test %>%
 # filter(Metric == "Degree", Real==1) %>% 
  ggplot(aes(x = NodeType, y = (value), fill = as.factor(Real))) + geom_boxplot() +
  facet_wrap(~Metric, scales = "free_y" )

test %>%
  filter(Metric == "Degree") %>% 
  group_by(NodeType,  Real) %>%
  summarise(mean = mean(value)) %>%
  spread(key = NodeType, value = mean)

test %>%
  mutate(Real = factor(Real)) %>%
  filter(Metric == "EntDeg_PowerFlow") %>%
  ggplot(aes(x = value, colour = Real)) + geom_density() +
  facet_wrap(~Metric, scales = "free_x") +scale_x_log10()
 
```


#Lost in scramble 

The amount of edges and nodes that are lost are quite small so I am not that botheres about correcting for it.
```{r}

EdgesNodesScramble <- 1:100 %>% map_df(~{
 
  print(.x)
 Sim_Order <- NewFunctionOrder  %>% select(-1) %>% pull(.x)
  
  g <- ReOrderGraph(gbase, Sim_Order)
  #calculate Flow
  g <- PowerFlow(g, "FECK40")
  #Make edges proportional to flow
  g <- Proportional_Load(g, alpha = 5)
  
  UselessEdge <- (get.edge.attribute(g, "PowerFlow")==0)

  print(get.edge.attribute(g, "name", index = (1:length(UselessEdge))[UselessEdge]) )
  #Remove Edges that are not doing anything and then any islanded nodes.
  #This is done before the simulation begins
  g <- delete.edges(g, (1:length(UselessEdge))[UselessEdge]) %>%
    BalencedGenDem(., "Demand", "Generation")

  tibble(Edges = ecount(g),
         Nodes = vcount(g),
         components = components(g)$no,
         Order = .x) 

})



EdgesNodesScramble %>%
  ggplot(aes(x = Edges)) + geom_density()

EdgesNodesScramble %>%
  ggplot(aes(x = Nodes)) + geom_density()


```

#Model Nodes


This section classifies nodes as Using transfer/Load/Gen
```{r}

#Creates 10 fold classification to predict the rol of each node as a binary classifier
 RangerPerf <-c("Generator", "Demand", "Transfer", "NodeType") %>% map_df(~{
 StandardVuln2 <- StandardVuln %>%
  select(GroupVar = .x, Degree:EntDeg_LinkLimit) %>% #Using pure topology
  #select(GroupVar = .x, Degree:EntDeg_PowerFlow, Elec_Centrality) %>% #using extended topo, e.g. cheating
  mutate(GroupVar = GroupVar*1) %>%
  mutate_all(function(Var){ifelse(is.finite(Var), Var, 0)})


trainset <- StandardVuln2 %>%
  filter(complete.cases(.)) 

folds <- trainset %>%
  select(GroupVar) %>%
  KfoldIndex(., 10)

test <- 1:10 %>% map_df(~{

Mod <- ranger(data = trainset[folds !=.x,],  dependent.variable.name = "GroupVar", classification = TRUE)

Preds<- predict(Mod, trainset[folds==.x,])

ModConf <- confusionMatrix(factor(Preds$predictions, levels = c(1,0)), factor(trainset$GroupVar[folds==.x], levels = c(1,0)))

 ModPerf <- tibble(name = c(names(ModConf$overall),names(ModConf$byClass)), 
                   value = c(ModConf$overall, ModConf$byClass), fold = .x)

 return(ModPerf)
}) %>% spread(key = name, value = value) %>%
  mutate(Type = .x)

})


RangerPerf %>%
  ggplot(aes(x = Type, y = Accuracy-AccuracyNull)) + geom_boxplot()

#these nodes are at the end of a thread but are neither generation or load... why?
test <- StandardVuln %>%
  filter(Transfer==TRUE, Degree==1) %>%
  left_join(trans1 %>% select(name = Bus.Name, Generation = BusTransferB))

#About 35% of the nodes at the end of a line that are transfer nodes are in fact small generators
table(test$Generation==0)

```


```{r}

TestOut <- c("Generator", "Demand", "Transfer") %>%
  map_df(~{
    
StandardVuln %>%
  rename(target = .x) %>%
  group_by(Degree, target) %>%
  summarise(counts = n()) %>%
  mutate(target = ifelse(target, "true", "false")) %>%
  spread(key = target, value = counts, fill = 0) %>%
      ungroup %>%
  mutate(PercOfNodes = true/(true+false),
         PercofTot = true/sum(true),
         cumsum = cumsum(PercofTot),
         Type = .x)
    
  })

TestOut %>%
  group_by(Type) %>%
  summarise(counts = sum(true))

TestOut %>%
  ggplot(aes(x = Degree, y = cumsum, colour = Type)) + geom_line()

StandardVuln %>%
  ggplot(aes(x = Degree)) + geom_histogram(binwidth = 1)



```

