---
title: "Rayshading UK topology"
author: "Jonathan Bourne"
date: "04/07/2019"
output: html_document
---


This code was lifted from the spring system project markdown file. It is entirely dependent on several chunks to run. mostly the setp up chunk the graph load chunk, the UK network plot chunk and the kriging chunk. 

It was removed from the code as it does not directly add to the core of the paper, although the animation can be added as a supplementary material.

#Rayshading

functions taken from

##this needs to be properly integrated and attributed
% https://github.com/wcmbishop/rayshader-demo/blob/master/R/rayshader-gif.R

```{r}
#' Build a gif of 3D rayshader plots
#'
#' @param hillshade Hillshade/image to be added to 3D surface map.
#' @param heightmap A two-dimensional matrix, where each entry in the matrix is the elevation at that point.
#' @param file file path for .gif
#' @param duration gif duration in seconds (framerate will be duration/n_frames)
#' @param ... additional arguments passed to rayshader::plot_3d(). See Details for more info.
#'
#' @details This function is designed to be a pipe-in replacement for rayshader::plot_3d(),
#' but it will generate a 3D animated gif. Any inputs with lengths >1 will 
#' be interpreted as "animation" variables, which will be used to generate 
#' individual animation frames -- e.g. a vector of theta values would produce
#' a rotating gif. Inputs to plot_3d() that are meant to have length >1 
#' (specifically "windowsize") will be excluded from this process.
#'
#' @return file path of .gif file created
#' 
#' @examples
#' # MONTEREREY BAY WATER DRAINING
#' # ------------------------------
#' # define transition variables
#' n_frames <- 180
#' waterdepths <- transition_values(from = 0, to = min(montereybay), steps = n_frames) 
#' thetas <- transition_values(from = -45, to = -135, steps = n_frames)
#' # generate gif
#' zscale <- 50
#' montereybay %>% 
#'   sphere_shade(texture = "imhof1", zscale = zscale) %>%
#'   add_shadow(ambient_shade(montereybay, zscale = zscale), 0.5) %>%
#'   add_shadow(ray_shade(montereybay, zscale = zscale, lambert = TRUE), 0.5) %>%
#'   save_3d_gif(montereybay, file = "montereybay.gif", duration = 6,
#'               solid = TRUE, shadow = TRUE, water = TRUE, zscale = zscale,
#'               watercolor = "imhof3", wateralpha = 0.8, 
#'               waterlinecolor = "#ffffff", waterlinealpha = 0.5,
#'               waterdepth = waterdepths/zscale, 
#'               theta = thetas, phi = 45)
#' 
save_3d_gif <- function(hillshade, heightmap, file, duration = 5, ...) {
  require(rayshader)
  require(magick)
  require(rgl)
  require(gifski)
  require(rlang)
  
  # capture dot arguments and extract variables with length > 1 for gif frames
  dots <- rlang::list2(...)
  var_exception_list <- c("windowsize")
  dot_var_lengths <- purrr::map_int(dots, length)
  gif_var_names <- names(dots)[dot_var_lengths > 1 & 
                                 !(names(dots) %in% var_exception_list)]
  # split off dot variables to use on gif frames
  gif_dots <- dots[gif_var_names]
  static_dots <- dots[!(names(dots) %in% gif_var_names)]
  gif_var_lengths <- purrr::map_int(gif_dots, length)
  # build expressions for gif variables that include index 'i' (to use in the for loop)
  gif_expr_list <- purrr::map(names(gif_dots), ~rlang::expr(gif_dots[[!!.x]][i]))
  gif_exprs <- exprs(!!!gif_expr_list)
  names(gif_exprs) <- names(gif_dots)
  message(paste("gif variables found:", paste(names(gif_dots), collapse = ", ")))
  
  # TODO - can we recycle short vectors?
  if (length(unique(gif_var_lengths)) > 1) 
    stop("all gif input vectors must be the same length")
  n_frames <- unique(gif_var_lengths)
  
  # generate temp .png images
  temp_dir <- tempdir()
  img_frames <- file.path(temp_dir, paste0("frame-", seq_len(n_frames), ".png"))
  on.exit(unlink(img_frames))
  message(paste("Generating", n_frames, "temporary .png images..."))
  for (i in seq_len(n_frames)) {
    message(paste(" - image", i, "of", n_frames))
    rgl::clear3d()
    hillshade %>%
      plot_3d_tidy_eval(heightmap, !!!append(gif_exprs, static_dots))
    rgl::snapshot3d(img_frames[i])
  }
  
  # build gif
  message("Generating .gif...")
  magick::image_write_gif(magick::image_read(img_frames), 
                          path = file, delay = duration/n_frames)
  message("Done!")
  invisible(file)
}


plot_3d_tidy_eval <- function(hillshade, ...) {
  dots <- rlang::enquos(...)
  plot_3d_call <- rlang::expr(plot_3d(hillshade, !!!dots))
  rlang::eval_tidy(plot_3d_call)
}


#' Create a numeric vector of transition values.
#' @description This function helps generate a sequence 
#' of numeric values to transition "from" a start point
#' "to" some end point. The transition can be "one_way" 
#' (meaning it ends at the "to" point) or "two_way" (meaning
#' we return back to end at the "from" point).
#'
#' @param from starting point for transition values
#' @param to ending point (for one-way transitions) or turn-around point 
#'           (for two-way transitions)
#' @param steps the number of steps to take in the transation (i.e. the length
#'              of the returned vector)
#' @param one_way logical value to determine if we should stop at the "to" value
#'                (TRUE) or turn around and return to the "from" value (FALSE)
#' @param type string defining the transition type - currently suppoerts "cos"
#'             (for a cosine curve) and "lin" (for linear steps)
#'
#' @return a numeric vector of transition values
#' 
transition_values <- function(from, to, steps = 10, 
                              one_way = FALSE, type = "cos") {
  if (!(type %in% c("cos", "lin")))
    stop("type must be one of: 'cos', 'lin'")
  
  range <- c(from, to)
  middle <- mean(range)
  half_width <- diff(range)/2
  
  # define scaling vector starting at 1 (between 1 to -1)
  if (type == "cos") {
    scaling <- cos(seq(0, 2*pi / ifelse(one_way, 2, 1), length.out = steps))
  } else if (type == "lin") {
    if (one_way) {
      xout <- seq(1, -1, length.out = steps)
    } else {
      xout <- c(seq(1, -1, length.out = floor(steps/2)), 
                seq(-1, 1, length.out = ceiling(steps/2)))
    }
    scaling <- approx(x = c(-1, 1), y = c(-1, 1), xout = xout)$y 
  }
  
  middle - half_width * scaling
}

```

##create 3D plot
```{r}

{
kriged_df3 <- kriged_df %>%
  rename(x = Longitude, y = Latitude) %>%
  mutate(Z = z/sd(z)) 
kriged_df3 <- kriged_df3 %>%
  spread(key = x, value = Z, fill = min(kriged_df3$Z)-2) 

x <- names(kriged_df3)[-1]  %>% as.numeric()
y <- kriged_df3 %>% pull(y)

kriged_df3 <- kriged_df3 %>%
  select(-y) %>% as.matrix()
}

elev_matrix <- (kriged_df3)*100

ambmat <- ambient_shade(elev_matrix, zscale = 20)
raymat <- ray_shade(elev_matrix, zscale = 20, lambert = TRUE)
watermap <- detect_water(elev_matrix)

elev_matrix %>%
  sphere_shade(texture = "imhof1") %>%
  add_water(watermap, color = "imhof4") %>%
  add_shadow(raymat, max_darken = 0.5) %>%
  add_shadow(ambmat, max_darken = 0.5) %>%
  plot_3d(elev_matrix, zscale = 20, theta = -45, phi = 45, water = FALSE,
          windowsize = c(1000,800), zoom = 0.75, waterlinealpha = 0.3,
          wateralpha = 0.5, watercolor = "lightblue", waterlinecolor = "white")
#%>% render_snapshot() # Save image to current path




```

##animate
```{r}
n_frames <- 180
zscale <-20
waterdepths <- transition_values(from = min(elev_matrix) + 2, to = 0, steps = n_frames) 
thetas <- transition_values(from = -65, to = -115, steps = n_frames)
# generate gif
elev_matrix %>% 
  sphere_shade(texture = "imhof1", zscale = 1) %>%
  add_shadow(raymat, max_darken = 0.5) %>%
  add_shadow(ambmat, max_darken = 0.5) %>%
  save_3d_gif(elev_matrix, file = "GB.gif", duration = 5,
              solid = TRUE, shadow = TRUE, water = TRUE, zscale = zscale,
              watercolor = "imhof3", wateralpha = 0.8, 
              waterlinecolor = "#ffffff", waterlinealpha = 0.5,
              waterdepth = waterdepths/zscale, 
              theta = thetas, phi = 45)




#orig
elev_matrix %>% 
  sphere_shade(texture = "imhof1", zscale = zscale) %>%
  add_shadow(raymat, max_darken = 0.5) %>%
  add_shadow(ambmat, max_darken = 0.5) %>%
  save_3d_gif(elev_matrix, file = "GB.gif", duration = 6,
              solid = TRUE, shadow = TRUE, water = TRUE, zscale = zscale,
              watercolor = "imhof3", wateralpha = 0.8, 
              waterlinecolor = "#ffffff", waterlinealpha = 0.5,
              waterdepth = waterdepths/zscale, 
              theta = thetas, phi = 45)

```
