---
title: "Untitled"
author: "Jonathan Bourne"
date: "22 March 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

Target journals
Physica A
Sustainable Energy, Grids and Networks
International Journal of Critical Infrastructure Protection


https://github.com/schochastics/graphlayouts

https://github.com/hackl/tikz-network


some IEEE datasets
https://icseg.iti.illinois.edu/power-cases/

annpotate points with rectangles
https://ggforce.data-imaginist.com/reference/geom_mark_rect.html

#Set up
```{r Setup}

packages <- c("tidyverse", #used everywhere 
              "igraph", #It's a graph project... let's be real
              "readr", #general csv loading
              "readxl", "broom", 
              "stringr", #various
              "xtable", #making a table of the network statistics
              "rlang", "animation", "caret", "rgdal", "sf", "gstat", "automap", "rayshader", 
              "minpack.lm", #used by the generate_toy_height_data function to find pairwise equilibrium
              "latex2exp", #needed to add latex symbols to plots
              "yardstick", #needed to for the performance metrics
              "gganimate", "tmaptools", "rgeos", "raster","ggraph", 
              "rsample", #used in sampling the data for gam modelling
              "cowplot", # some of the plots need specific structuring provided by cowplot
              "mgcv" #Used for the gam modelling
              )

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

select <- dplyr::select
arrange <- dplyr::arrange
sapply(packages, library, character.only = TRUE)

library(PowerGridNetworking)
library(rSETSe)
library(RobustnessInternal)

#Set up file system to read the correct folders this switches between aws and windows mode

basewd <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder"
CodeFolder <- "/home/jonno/setse_and_network_robustness"
datafile <- "/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder/ETYSAppendixB"
LatexFolder <- "/home/jonno/Dropbox/Apps/ShareLaTeX/Sets Paper 2" 
FiguresFolder <- file.path(LatexFolder, "Figures")
TablesFolder <- file.path(LatexFolder, "Tables")
MatricesFolder <- file.path(LatexFolder, "Matrices")
Tariff <- file.path(basewd,"Tariff and Transport")
#PLwd <- "/media/jonno/Seagate Expansion Drive/System_Dynamics"
Deletion_Order_Folder <-  file.path("/home/jonno/Dropbox/AWS_Simulation_Files") #Only one of the deletion order folders is needed. Either Nodes or Edges
project_folder <- "/home/jonno/Dropbox/IEEE_Networks" #"/media/jonno/Seagate Expansion Drive/IEEE_Networks"
embeddings_path <- file.path(project_folder, "embeddings")
power_grid_graphs_path <- file.path(project_folder, "power_grid_graphs") 

#Load some other useful functions
list.files("/home/jonno/Useful_PhD__R_Functions", pattern = ".R", full.names = T) %>%
  walk(~source(.x))

#The calc_spring_constant needs to be temporarily overloaded due to a really annoying bug that I have discovered just at CRAN acceptance... OMG!
calc_spring_constant <- function(g, youngs_mod = "E", A = "Area", distance = "distance"){
  
 youngs_mod_vect <- igraph::get.edge.attribute(g, name = youngs_mod)*igraph::get.edge.attribute(g, name = A)/
   igraph::get.edge.attribute(g, name = distance)

  g2 <- igraph::set.edge.attribute(g, "k", value = youngs_mod_vect
                                   #temp$k
                                   )
  return(g2)
}

```


#Set up UK Graph and SETSe

This is used at several points in the paper.

The real UK limits is plotted on top of the redistributed points

The UK network elevation and strain is plotted as a kriged map of the UK

```{r}

{UKg <- readRDS(file.path(power_grid_graphs_path,  paste0("UK_high_voltage.rds"))) %>%
            #    Proportional_Load(., 1, PowerFlow = "power_flow", Link.Limit = "edge_capacity") %>%
                set.edge.attribute(. , "distance", value = 1) %>%
        set.edge.attribute(., "Area", value = 1) %>%
        calc_spring_youngs_modulus(., "power_flow", "edge_capacity", 
                                   minimum_value = 10000, stretch_range = 1000) %>%
        calc_spring_constant(., youngs_mod ="E", A = "Area", distance = "distance") %>%
        normalise_dc_load(.,  
                           generation = "generation", 
                           demand  = "demand",
                           net_generation = "net_generation", 
                           capacity = "edge_capacity",
                           edge_name = "edge_name", 
                           node_name = "name",
                           power_flow = "power_flow")  %>%
  #prevents NaNs when edge capacity is zero
  set_edge_attr(., "edge_capacity", 
                value = ifelse(is.finite(edge_attr(.,"edge_capacity")), edge_attr(.,"edge_capacity"), 0 ) ) 

}


#useful at various stages
energy_types <- c("Coal", "Gas", "Renewable", "Nuclear")
sim_names <- paste0("No_", energy_types)

#takes about 60 secs
UK_SETSe_data <- SETSe_auto(UKg, 
           force ="net_generation", 
           distance = "distance", 
           edge_name = "edge_name",
           tstep = 0.01, 
           mass = 1, 
           max_iter = 100000, 
           tol = 2e-3,
           sparse = FALSE,
           hyper_iters = 100,
           sample = 100,
           verbose = T)


  line_load_df  <-   as_data_frame(UKg) %>%
    mutate(line_load =abs(power_flow)/edge_capacity)
  
  UK_SETSe_data$edge_embeddings <- UK_SETSe_data$edge_embeddings %>%
    left_join(line_load_df %>% select(edge_name, line_load)) %>%
    mutate(alpha = 1/line_load)

  sum(abs(UK_SETSe_data$node_embeddings$static_force))
  
  mean(UK_SETSe_data$edge_embeddings$tension)

  cor(UK_SETSe_data$edge_embeddings %>% select(tension:alpha), use = "pairwise.complete.obs")
  
```


#Psychadelic beard/boat

This plots the strain values of a 4 node three edge graph with a constant EC and varying alpha. It shows that strain is more expressive than either alpha, ec or a combination of the two

The code giveing the animation that shows convergence has been lost. The animation is pretty helpful so it is a good idea to do it again.
```{r}

toy_height_data <- generate_toy_height_data()


  toy_height_data$toy_height_data %>%
    # some of the mean_alpha values are seperating on machine tolerance or something
        mutate(mean_alpha = signif(mean_alpha,5)) %>% 
    #filter(mean_alpha <=2.5) %>%
    ggplot(aes(x = ratio, y = mean_strain, colour = mean_alpha, group = mean_alpha)) + 
    geom_line(size = 1) +
    scale_colour_viridis_c() +
    labs(title ="Strain and System Tolerance in terms of capacity fraction in edge B", 
         y = "System Strain", 
         x= latex2exp::TeX("$\\frac{\\tau_{B}}{\\tau_{B}+\\tau_{C}}$"),
         colour = "System \ntolerance") #latex2exp::TeX(paste("system", "$\\alpha$"))
  ggsave(file.path(FiguresFolder, "Constant_excess_capacity.pdf"))
  
  #A plot of the entropy of the system
  #I am not sure how useful this is. It may be removed
    toy_height_data$entropy_data %>%
  ggplot(aes(x = div, y = mean_strain, colour = mean_alpha, group = mean_alpha)) + 
  geom_line(size = 1) +
  scale_colour_viridis_c() +
  facet_grid(~type) +
  labs(title = "The relationship between strain, system tolerance and entropy", 
       x = "Normalised entropy", 
       y ="system strain", 
       colour =  "Sytem tolerance")
ggsave(file.path(FiguresFolder, "entropy_theta.pdf"))

```

#Get network statistics

IEEE-118 and IEEE-300 have substantially more negative assortativity than the other networks, however the assortativity is still quite close to 0. Also we see that IEEE-118, IEEE-300 and the UK high voltage network have much larger mean distances between nodes than the other networks, htey also have the smallesting clustering coefficient.

As the error spikes appear on all the large network then they may be associated with the clustering or the distance.

This could then be tested by creating networks on an assortivity/clustering distance scale and trying to re-create the spikes. This would then help understand which metric would be most appropriate as a proxy for robustness
```{r}
network_summary_stats <-create_powergrid_network_statistics(list.files("/home/jonno/Dropbox/IEEE_Networks/power_grid_graphs", pattern = ".rds", full.names = T))

network_summary_stats %>%
  xtable(caption = "Summary statisitics of the 6 power networks used in the study",
         label = "tab:net_stats")

```


#Plot embedded networks

This chunk loads the PL=5 embeddings for each network and plots them using Fruchtman-Reingold.

```{r}
create_union_of_power_grids() %>%
  ggraph(., layout = "stress") +
  geom_edge_fan() +
  geom_node_point(aes(colour = elevation))+
scale_color_viridis_c()+
  facet_nodes(~factor(type, 
                      levels = c("IEEE 14", "IEEE 30", "IEEE 57", "IEEE 118", "IEEE 300", "UK high voltage" )), 
              scale = "free") +
  labs(title = "All networks showing elevation embeddings proportioanlly loaded to PL=5")
  
ggsave(file.path(FiguresFolder, "all_networks.pdf"))

```


#all_graph_agg
Load all collapse data

```{r}
all_graph_agg <- list.files("/home/jonno/Dropbox/IEEE_Networks/attacks", full.names = T, recursive = T) %>%
  map_df(~{
    
    file_path <-.x
    read_rds(file_path) 
  }) %>% 
  group_by(carrying_capacity, smallest, largest, fract, robin_hood_mode, graph) %>%
  summarise_all(mean) %>%
  ungroup %>%
  mutate(mean_alpha = 1/mean_alpha,
         median_alpha = 1/median_alpha) %>%
  select(-median_alpha) %>%
  mutate(carrying_capacity = signif(carrying_capacity),
         smallest = signif(smallest),
         largest = signif(largest),
         fract = signif(fract))

PL_SETSe_emebeddings <- process_all_pl_setse_emebeddings( strain_folders = file.path(embeddings_path, "PL"),
                                                          attack_folders = "/home/jonno/Dropbox/IEEE_Networks/PL_attacks")

```

```{r}
#these are the evaluation metrics of the system
multi_metric <- metric_set(rmse, rsq, mae, smape)
```


#Aggregate and plot IEEE-118 r,c data
This plot shows how setse reacts to different starting parameters.
Answer not a lot and also it is symmetrical

This is only used in the appendix
```{r}
#N.B.
#The mean and median strain is the value at the loss of gc point. The correct value comes in when the strain data is added

#using the combined data frame aggregate the results by parameter group
source(file.path(CodeFolder, "sub_scripts", "process_rc_comparisons_subscript.r"))

#Raster plot that shows how r and c affect model performance
metric_performance %>%
  filter(average_type=="mean",
         .metric %in% c("rsq", "smape"),
         metric %in% c("tension", "strain")
         ) %>%
  #mutate(metric == ifelse())
  group_by(.metric) %>%
  mutate(perc = ifelse(.metric =="rsq",rank(signif(-.estimate, 3)), rank(signif(.estimate, 3))),
         perc2 = .estimate/min(.estimate),
         perc2 = ifelse(perc2>2, 2, perc2)-1
         ) %>% 
  ggplot(aes(x = factor(r), y = factor(c, levels =rev(10^(1:5))), fill= perc2, )) + geom_raster() +
  facet_grid(metric~.metric) +
  geom_text(aes(label = signif(.estimate, 3))) +
    scale_fill_viridis_c(limits = c(-1, 1)) +
    labs(title = "Model performance mean tension across multiple metrics by k range and minimum k value", 
       x = "range of k", 
       y = "minimum k value",
       fill = "relative error")
ggsave(filename = file.path(FiguresFolder, "randc_performance_mean_tension.pdf"))
```

The results of the r c analysis show that the mean value of tension and strain is much more accurate than the median. What's more the matrices produced by the mean and median values are symmetric (given small variances due to convergence differences) about the minor diagonal. All the model values are equal on the Major diagonal where r = c.

The mae and rsq values are almost identical for all rc combos. the min/max is mae (0.97) rsq (0.99), for rmse there is a small difference 0.93 only smape has any substantial differences 0.82. It is worth remembering that these changed are over a search space of 3 orders of magnitude. Some of the difference could be due to differences in the residual force due to convergence.

This means that a good choice for r and c would r 1000 c = 100 or r = 10k c = 1000


#Model across all graphs

After demonstrating the effectiveness on a single graph this chunk loads the data from all graphs used in the analysis.

##SETSe embeds

```{r}

non_PL_folders <- list.files(embeddings_path, full.names = T)[!grepl("PL", list.files(embeddings_path))]

all_SETSe_emebeddings <- process_all_setse_emebeddings(
  processed_path =  file.path(project_folder, "all_setse_embeddings_standard.rds"), 
  folder_paths = non_PL_folders, 
  graph_agg= all_graph_agg)

```

##Steller embeds

```{r}
stellar_embeds <- c("DGI", "node2vec") %>%
  map_df(~{
     folder_path <- file.path(project_folder, "embeddings", .x, "dimensions_32")
    stellar_embeddings_loader(folder_path) %>%
      mutate(metric = .x)
    
  }) %>% 
  left_join(. ,all_graph_agg %>%
  select(graph, carrying_capacity:robin_hood_mode, attack_round) %>%
  mutate(graph = str_remove(graph, "_igraph")) ) %>%
  mutate(average_type = "mean")


stellar_embeds_pl <- c("DGI_pl", "node2vec_pl") %>%
  map_df(~{
    file.path(project_folder, "embeddings", .x) %>%
      stellar_embeddings_loader_pl() %>%
      mutate(metric = str_remove(.x, "_pl"))
    
  })

#You can call this if you want but it is an ugly mess for the stellar pl embeds
#They are all over the place
# temp <- stellar_embeds %>% 
#   select(value = edge_mean_length, fract:average_type) %>%
#   mutate(type = "base") %>%
#     bind_rows(stellar_embeds_pl %>% 
#                 select(graph, carrying_capacity, value, metric) %>%
#                 mutate(type = "pl")) %>%
#      group_by(graph, metric) %>%
#      mutate(
#        value = kappa(value),
#          robin_hood_mode = as.character(robin_hood_mode)) %>%
#      ungroup 
# 
# stellar_embeds_pl <- temp %>% filter( type == "pl")
# stellar_embeds <- temp %>% filter( type != "pl")
```


##plot results

This is one of the key plots of the paper. It shows how well each of the metrics tracks the collapse point of the network
```{r}


pl_plot_df <- PL_SETSe_emebeddings %>%
                 filter(graph == "IEEE_118_igraph",
                        carrying_capacity !=1.010,
                        average_type == "mean")

# Add in the pl stellar if you want but yikes what a horror show. 
# pl_plot_df <- pl_plot_df %>% select(graph, carrying_capacity, average_type, attack_round) %>%
#   distinct() %>%
#   mutate(graph = str_remove(graph, "_igraph")) %>%
#   left_join(stellar_embeds_pl %>% select(graph, carrying_capacity , value, metric)) %>%
#   bind_rows(pl_plot_df %>% select(graph, carrying_capacity , value, metric, average_type, attack_round))


  stellar_embeds %>% 
     group_by(graph, metric) %>%
     mutate(
       value = kappa(value),
       average_type = "mean",
         robin_hood_mode = as.character(robin_hood_mode))%>%
     bind_rows(. ,
               all_SETSe_emebeddings %>%
                 mutate(graph = str_remove(graph, "_igraph"))
     ) %>%
     filter(
       graph == "IEEE_118",
       grepl("mean", average_type),
       metric !="elev"
       #average_type == average_type2
     ) %>%
     #select(metric, value, attack_round, metric, carrying_capacity)
     mutate(metric = str_replace(metric, "_", " "),
            error_spike = carrying_capacity>1.5 & as.logical(robin_hood_mode) & fract == 1) %>%
     ggplot(aes(x = value, y = attack_round, group = metric)) + 
     geom_point(aes( colour =  as.factor(carrying_capacity))) +
     geom_line(data = pl_plot_df, size = 1) +
     geom_smooth(method = "gam",se = FALSE) +
     facet_wrap(~metric) +
     #facet_wrap(~metric, scales = "free_x") +
     labs(colour = "Capacity", y = "Attack round", x = "Fraction of total range")+
     labs(title = "The relationship between robustness metrics and number of attacks until failure",
          y = "Number of rounds until loss of giant component") 
ggsave(file.path(FiguresFolder, "robustness_and_attacks_118.pdf"))

```

##Error spikes fraction
The output of this plot just calculates the fraction of results that are in the error spikes. It is used as a comment in the paper.

The biggest spikes are when the distribution fraction is 1 and robin hood mode is true. Each individual spike is made up of one of the "largest" fractions the highest spike is 0.1 the smallest is 0.5. This is becuase the more extreme the value the more concentrated the result.
 #SETSe is a poor proxy for failure when the edges with the most flow have the least excess capacity and the edges with the least flow have the most excess capacity at the same time that the network overall has a low likelihood of cascades in general. In this situation the SETSe algorithm predicts cascading failures where there are unlikely to be any underestimating the robustness of the network. However this only occurs when the network has a relatively large number of edges that are not part of a cycle
 
What's more these situations are unlikey to occur as the excess capacity tends to be larger on edges with lots of flow. see that guy I cited previously.

more detailed information on error spikes can be found in the non-core markdown script under the section `error plot`


```{r}
#The error spikes are responsible for only 6% of the total number of cases
all_SETSe_emebeddings %>%
  mutate( error_spike = carrying_capacity>1.5 & as.logical(robin_hood_mode) & fract == 1) %>%
  group_by(error_spike) %>%
  summarise(count = n()) %>%
  mutate(perc = count/sum(count))

```


#Get performance across all networks

This chunk creates the performance metrics of all different methods.
Mean loading and mean tension outperform the others so much only they are included.
The Stellar embeddings are not at all stellar

Model that used tension and loading was tested and was generally better. However, I didn't feel it really added any value to the paper and so removed it. That code can be found in the non-core markdown

```{r}
multi_metric <- metric_set(rmse, rsq, mae, smape)
#This looks at the metrics as a raw proxy for robustness
#It takes a while so is loaded when possible
if(!file.exists(file.path(project_folder, "setse_performance_df.rds"))){
  
 setse_performance_df <- cross_validated_setse_embeddings(all_SETSe_emebeddings, PL_SETSe_emebeddings)
  
  saveRDS(setse_performance_df, file = file.path(project_folder, "setse_performance_df.rds")) 
  
} else{
  
 setse_performance_df <- readRDS(file.path(project_folder, "setse_performance_df.rds"))
  
}

if(!file.exists(file.path(project_folder, "steller_performance.rds"))){
  
 steller_performance <- cross_validated_stellar_embeddings(stellar_embeds)
  
  saveRDS(steller_performance, file = file.path(project_folder, "steller_performance.rds")) 
  
} else{
  
 steller_performance <- readRDS(file.path(project_folder, "steller_performance.rds"))
  
}

#THe Stellar embeds were so bad it messes up the plot
setse_performance_df  %>%
#  bind_rows( steller_performance %>% mutate(graph_order = graph, combo = metric) ) %>%
  filter(eval_metric %in% c("rsq", "smape")) %>%
  ggplot(aes(x = graph_order, y = .estimate, fill = metric)) + geom_boxplot() +
  facet_wrap(~eval_metric, scales = "free_y") +
  theme(axis.text.x = element_text(angle = 15, hjust = 1))  +
  labs(title = "Comparing loading and tension as robustness metrics",
       y = "Evaluation metric score",
       x = "Networks in order of nodes",
       colour = "robustness metric") 
ggsave(filename = file.path(FiguresFolder, "performance_across_networks.pdf"))

```

### Anova

This chunk performs an anova on the error dataset just to confirm that Tension really is better. The results of this chunk are used as comments in the paper
```{r}
#Tension has significantly lower error when accounting for graph type and evaluation metric
error_aov_prep <- setse_performance_df %>%
  filter(eval_metric %in% c("rsq", "smape")) %>%
  #  group_by(eval_metric, graph_order) %>%
  mutate(.estimate = ifelse(eval_metric =="rsq", 1/.pl_estimate, .pl_estimate) #%>% {(.-mean(.))/sd(.)}
  ) %>%
  rename(estimate = .pl_estimate)

aov_res <-aov(estimate ~  metric + graph_order+ eval_metric, data = error_aov_prep )
summary(aov_res)

setse_performance_df %>%
  group_by(eval_metric, metric, average_type) %>%
  summarise(all_data = mean(.estimate),
            pl_data = mean(.pl_estimate))

#this is removed as it is quick to make and is not used again
rm(error_aov_prep); rm(aov_res)
```

#UK map 

This chunk plots the UK high voltage network in geospace and shows how SETse provides interpretable results.

```{r}
shapefile <- file.path("/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder/ShapeFiles UK",
                       "Countries_December_2017_Ultra_Generalised_Clipped_Boundaries_in_UK_WGS84.shp")

GB <- st_read(shapefile) %>%
  filter(ctry17cd !="N92000002") %>%
  st_union()

spdf <- as(GB, "Spatial") %>% st_as_sf %>%
  st_crop(c(xmin = -7.5, ymin = 50, xmax = 2, ymax = 59)) %>%
  as_Spatial()

kriged_height_strain_data <- krige_SETSe_maps(                                                      
  SETSe_list = UK_SETSe_data, 
  coords = MakeMapDF(UKg, read_csv(file.path("/home/jonno/Dropbox/Jonathan_Bourne_Phd_Folder", "point.csv")))  %>%
    filter(PositionType=="Geo Space"), 
  spatial_df = spdf)

kriged_height_strain_data %>%
  mutate(type = fct_relevel(type, "Line Load", after = Inf)) %>%
  ggplot(aes(x=Longitude, y=Latitude)) + 
  geom_tile(aes(fill=value_perc)) + coord_equal() +
  facet_grid(~type) +
  scale_fill_viridis_c() +
scale_colour_viridis_c(option = "plasma") +
  labs(title = "Elevation and Tension of the UK high-voltage power grid under base load generation", 
       fill = "Percentile") +
  theme(axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "bottom",
        plot.margin=unit(c(-0,0,-0,0),"mm")
        ) #the legend position may want changing back to the more convential side.
  ggsave(file.path(FiguresFolder, "BritainKrigedTopology2.pdf"), dpi = 600,
         width = 8.99, height = 4) #Thisto make the aspect ratio better


```


#Optional Failure groups
The code for the 10k attacks was moved to the non-core section nothing was found and it was a nightmare

#Update packages

```{r}
library(devtools)
library(roxygen2)
```

rsetse update
```{r}
roxygenise( "~/rSETSe")
detach("package:rsetse", unload = TRUE)
install("~/rSETSe")
library(rsetse)
```

RobustnessInternal update
```{r}
roxygenise( "~/setse_and_network_robustness/RobustnessInternal")
detach("package:RobustnessInternal", unload = TRUE)
install("~/setse_and_network_robustness/RobustnessInternal")
library(RobustnessInternal)
```

