---
title: "Untitled"
author: "Jonathan Bourne"
date: "22/10/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---


stplanr R package for transport
https://docs.ropensci.org/stplanr/articles/stplanr-od.html


Origin destination data for London
http://passenger.data.tfl.gov.uk/


Some bike share stuff that can be used. has data and code. Might only need projection
https://urbandatacyclist.com/2018/03/15/predicting-route-preferences-in-bike-sharing/
#Set up
```{r}
packages <- c("rlang", "tidyverse", "igraph", "devtools", "minpack.lm")

new.packages <- packages[!(packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages)

sapply(packages, library, character.only = TRUE)



#install_github("JonnoB/PowerGridNetworking")
library(PowerGridNetworking)

#Set up file system to read the correct folders this switches between aws and windows mode

#creates the correct root depending on whether this is on the cloud or not
if(dir.exists("/home/jonno")){
  #This folder is for use on my machine
  project_folder <- "/home/jonno/Dropbox/IEEE_Networks"
  basewd <- "/home/jonno"
}else{
  #This is for the folder that is on the cloud
  project_folder <- "~/Dropbox/IEEE_Networks"
  basewd <- "~/Dropbox"
}

power_grid_graphs_path <- file.path(project_folder, "power_grid_graphs") #The path where the base igraph representations of the power grids are
collapse_sets_path <- file.path(project_folder, "collapse_sets") #the full collapse set of each power grid and the permutations are stored here
collapse_set_summaries_path <- file.path(project_folder, "collapse_set_summaries")
permuted_IEEE_118_path <- file.path(power_grid_graphs_path, "Permuted_IEEE_118") #The permuted base IEEE-118 igraphs are stored here
pl_IEEE_path <- file.path(power_grid_graphs_path, "pl_IEEE") 
edge_scramble_keys_path <- file.path(project_folder, "edge_scramble_keys")
edge_scramble_keys_IEEE_permutation_path <- file.path(edge_scramble_keys_path, "Permuted_IEEE_118")
analysis_parameter_file_path <- file.path(project_folder, "analysis_parameter_files")
HPC_startup_parameter_file_path <- file.path(project_folder, "HPC_parameter_files")
embeddings_path <- file.path(project_folder, "embeddings") 

#make sure all the paths exist
ls(pattern = "_path") %>% walk(~{
  if(!file.exists(.x)) dir.create(.x, recursive = T)
})

#Load some other useful functions
list.files(file.path(basewd, "Useful_PhD__R_Functions"), pattern = ".R", full.names = T) %>%
  walk(~source(.x))

list.files(file.path(basewd, "Flow_Spring_System"), pattern = ".R", full.names = T) %>%
  walk(~source(.x))


##
##
## These are the ec values that will be used and also the fraction of total scrambles that will be used in the analysis
##
##

#The alpha/ec values to scramble
Scramble_ec_values <- c(1.005, 1.025, 1.05, 1.1, 1.2, 1.5, 2, 3, 5, 7, 10, 20) 

#The fraction of edges that will be scrmabled for each scrambled alpha
fract_vect <- c(1, 0.75, 0.5, 0.25) #0.75 can also be added but may overlap with the others too much


```



#Create permuted IEEE-118 networks
```{r}
#Create a list of IEEE-118 networks where the demand and gen node values are internally permuted
set.seed(1235)
random_seeds <- sample(1:10000, 30)

g <- readRDS(file.path(power_grid_graphs_path, "IEEE_118_igraph.rds")) 

 
Permuted_IEEE_118_list <- random_seeds %>% map(~{
  g <- permute_gen_dem(g, .x)
  
  g <-  BalencedGenDem(g, 
                        Demand = "demand",
                        Generation = "generation",
                        OutputVar = "net_generation")
  
  SlackRef <- SlackRefFunc(g, name = "name", Generation = "generation")
  
  g <- PowerFlow(g, SlackRef$name, EdgeName ="edge_name", VertexName = "name", Net_generation = "net_generation", power_flow = "power_flow")

})

#Save the networks so that they can be used by the HPC 

1:length(Permuted_IEEE_118_list) %>%
  walk(~{
    saveRDS(Permuted_IEEE_118_list[[.x]], 
            file.path(permuted_IEEE_118_path, 
                      paste0("Permutation_", .x, ".rds")))
  })

#clean up the workspace. The graphs can just be loaded when needed
rm(g); rm(Permuted_IEEE_118_list)


```


#Create edge scrambles

Create the edge scrambles that give a range of alpha values for each initial ec/alpha value

returns a data frame that contains (amongst other things), a random seed and the associated alpha value. The network edges are scrambled using that random seed.

*N.B*
This chunk requires a large number of networks to be loaded and analysed so takes a long time. doing this in parallel is reccomended. However, I haven't been able to make it work effectively so keep it in serial

```{r}
networks_in_project <- list.files(power_grid_graphs_path, recursive = T)

for(n in 1:length(networks_in_project)){
          
          #load the graph for the edge scrambles to be calculated
          g <- readRDS(file.path(power_grid_graphs_path, networks_in_project[n]))
          
          #only creat the target orders if neces  sary
          if(file.exists(file.path(edge_scramble_keys_path, networks_in_project[n]))){
            
            print("file exists continuing to next network permutation")
          } else{
            
            target_orders_temp <- create_target_orders_for_strain_test(g, fract_vect, Scramble_ec_values,
                                                                       total_sample_space = 10000, #Larger number mean bigger extremes but it takes much longer. I choose 10k as a painful slow medium
                                                                       required_samples_out = 10,
                                                                       seed = n ) #previously a constant 123
            
            saveRDS(target_orders_temp, file.path(edge_scramble_keys_path, networks_in_project[n]))
          }
          
}


#testing output of variables
 g <- readRDS(file.path(power_grid_graphs_path, networks_in_project[1]))
 
 target_orders_temp <- create_target_orders_for_strain_test(g, c(0.25, 0.5, 0.75, 1), 1.5,
                                                            total_sample_space = 10000, 
                                                            required_samples_out = 10,
                                                            seed = 3 ,
                                                            subselect = FALSE) 
 #mean loading is perfectly normally distributed! wot dis!?
 #absolutely tiny sd. classic central limit theorem.
 #Is there a way to distort the distribution?
 target_orders_temp %>%
   ggplot(aes(x =mean_loading,
              colour = factor(fract))) +
   geom_density()
 
 target_orders_temp %>%
   ggplot(aes(x = mean_loading, y = mean_alpha, colour = factor(fract))) + geom_point()
 
 #use data from the embeddings, this comes from the 118 analysis script
   embeddings_list <- read_rds("/home/jonno/Dropbox/IEEE_Networks/test_strain/IEEE_118_igraph/fract_1_ec_7_v_10.rds" )
 
   test <- read_rds(file.path(edge_scramble_keys_path, "IEEE_118_igraph.rds")) %>%
     filter(ec == 7, v %in% c(1,10), fract == 1)
   
edge_embeddings <- embeddings_list$edge_embeddings
  


    g <- Proportional_Load(g, alpha = ec, PowerFlow = "power_flow",
                             Link.Limit = "edge_limit")
    
    edge_order_df <- create_scrambled_edges(g, scramble_seed, fract = fract)
```

#Create parameter dataframe

Base and strain HPC start up needs to be made for the permutations and the non-scramble

The parameter dataframe allows for efficient parallel processing of the large number of simulations performed in this project.

The parameter dataframe is saved to be used later on a different system such as an HPC or cloud machine.

The three code chunks should be combined into a single chunk as the differences between them are clearly minimal. This is a low priority though


The HPC parameter Array is different for the collapse set and the strain set the strain set is 480 simulations per set these are broken into 12 compute groups the numbers of the compute groups need to be specified before hand they are
1  101  201  301  401  501  601  701  801  901 1001 1101 this means that there is a different startup parameter file for strain and collapse.

##Permuted edges

This is ONLY the IEEE-118 power flow network. It has the edges scrambled/permuted AND load and demand 

```{r}
parameter_df <- generate_simulation_parameter_df(edge_scramble_keys_IEEE_permutation_path, 
                                             permuted_IEEE_118_path,
                                             collapse_sets_path,
                                             collapse_set_summaries_path,
                                             embeddings_path,
                                             replace_target_order = NULL) %>%
  mutate(graph_path = file.path("power_grid_graphs", graph_path))

save_params_for_HPC(parameter_df = parameter_df, HPC_startup_parameter_file_path, analysis_parameter_file_path)


saveRDS(parameter_df, file.path(analysis_parameter_file_path, "IEEE_118_permutation_parameter_file.rds"))
```

##Base edge scramble codes

This is ALL the IEEE power flow networks. They have the edges scrambled but the load and demand is NOT permuted

```{r}
parameter_df <- generate_simulation_parameter_df(edge_scramble_keys_path, 
                                             power_grid_graphs_path,
                                             collapse_sets_path,
                                             collapse_set_summaries_path,
                                             embeddings_path,
                                             replace_target_order = NULL)

save_params_for_HPC(parameter_df = parameter_df, HPC_startup_parameter_file_path, analysis_parameter_file_path)

#
#Params for a simple HPC test
#
#test run for HPC
#is an array of two attack only
test_params <- parameter_df %>%
  filter(permutation== "IEEE_118_igraph",
         simulation_id %in% 1) %>% filter(compute_group %in% 1:2) %>%
  mutate(permutation = paste0("test_", permutation))

#The HPC start up array
test_attack_startup <- test_params %>%
  distinct(compute_group) %>% 
  mutate(load_file = "test_base_IEEE_118_igraph.rds") 


saveRDS(test_params, 
        file.path(analysis_parameter_file_path, 
                  "test_base_IEEE_118_igraph.rds")) 

#save the parameter files for the attack simulations
write_delim(test_attack_startup, 
            path = file.path(HPC_startup_parameter_file_path, 
                             paste0("test_attack_", 
                                    gsub(".rds", ".txt","base_IEEE_118_igraph.rds"))), 
            delim = " ") #save the HPC start up parameter file. This defines the entire array
```

##non scrambled edges

The non-scrambled edges can be identified as they have fract_0


These parameter files are currently overwriting the parameter files of the main model. How can I get them to stop doing this?
```{r}



c(1, 1.02, 1.01, 1.005, 1.05, 1.1, 1.2, 1.5, 2, 2.5, 3, 5, 7, 10, 15, 20, 50, 100, 200, Inf)

non_scramble_df <- tibble(
  seed = NA,
  alpha =  c(1.005, 1.025, 1.05, 1.1, 1.2, 1.5, 2, 3, 5, 7, 10, 20) ,
  ec = alpha,
  v = 1,
  fract = 0)

parameter_df <- generate_simulation_parameter_df(edge_scramble_keys_path, 
                                             power_grid_graphs_path,
                                             collapse_sets,
                                             collapse_set_summaries_path,
                                             embeddings_path,
                                             replace_target_order = non_scramble_df) %>%
  mutate(compute_group = simulation_id)

save_params_for_HPC(parameter_df = parameter_df, HPC_startup_parameter_file_path, analysis_parameter_file_path)
```



#Load the collapse set summaries
```{r}


test <- read_delim(file.path(HPC_startup_parameter_file_path, ))

Permuted_IEEE_118_results <- list.files(path = "/home/jonno/Dropbox/IEEE_Networks/test_collapse",#collapse_set_summaries_path, 
                                        # pattern = ".rds", I saved them wrong, the code has been corrected but not re-run
                                        full.names = TRUE, 
                                        recursive = TRUE) %>%
  map_df(~read_rds(.x)%>%
           mutate(file_path = .x))   %>%
  arrange(-TotalNodes) %>%
  mutate(has_gc = mean_degree_sqrd > 2*mean_degree) %>%
  filter(!has_gc) %>%
  group_by(file_path) %>%
  summarise_all(first)  %>%
  #### This is not necessary after re-calc as all the info is included with the extracted data
  # left_join(parameter_df %>% 
  #             select(file_path  = collapse_summary_path, 
  #                    ec:permutation), by  = "file_path") %>%
  ###
  group_by(ec, v, fract, permutation) %>%
  summarise(NodesAttacked = mean(NodesAttacked)) 


##After this the strain needs to be added

parameter_df %>%
  filter(v == 1, fract == 1, permutation == 1, simulation_id==1) %>%
  pull(alpha)


g <- readRDS(file.path("/home/jonno/Dropbox/IEEE_Networks/power_grid_graphs/Permuted_IEEE_118/", "Permutation_1.rds")) %>%
  Proportional_Load(., alpha = 20)

edge_order_df <- Create_scrambled_edges(g, 2798, fract = 1) %>%
  mutate(loading = 1/alpha)

test <- edge_order_df %>%
  summarise(mean_alpha = mean(alpha),
            median_alpha = median(alpha),
            mean_loading = mean(loading),
            median_loading = median(loading))

```


#load robin hood data

make everything right then sim the last few bits


```{r}


file_path <-   "/home/jonno/HPC_jobs/IEEE_118_igraph/fract_0.25_ec_1.005_largest_0_smallest_0_robin_hood_FALSE/simulation_id_11.rds"
.x <- file_path

IEEE_118_results <- list.files(path = "/home/jonno/HPC_jobs/IEEE_118_igraph", 
                                        full.names = TRUE, 
                                        recursive = TRUE) %>%
  map_df(~{read_rds(.x) %>%
           mutate(file_path = dirname(.x)) %>%
  arrange(-nodes) %>%
  mutate_at(.vars = 5:8, .funs = first) %>%
  mutate(has_gc = mean_degree_sqrd > 2*mean_degree) %>%
  filter(!has_gc) %>%
  slice(1)
    })


#The previous takes a long time so an rds should be saved for speed
saveRDS(IEEE_118_results, file = file.path("/home/jonno/Dropbox/IEEE_Networks", "IEEE_118_attack_results") )



IEEE_118_agg_res <- IEEE_118_results %>%
  group_by(file_path) %>%
  summarise_all(mean) %>%
  mutate(mean_alpha = 1/mean_alpha,
         median_alpha = 1/median_alpha) %>%
  select(-median_alpha) %>%
  mutate(carrying_capacity = signif(carrying_capacity),
         smallest = signif(smallest),
         largest = signif(largest),
         fract = signif(fract))


test <- IEEE_118_agg_res  %>% #there is an error on 118 where mean alpha and median alpha is equal. However, this is not important as median_alpha and median_load are identical anyway. As such median alpha can be removed
  pivot_longer(., cols = c("mean_loading", "median_loading", "mean_alpha"), names_to = "metric" )



test %>%
   filter(
          #!robin_hood_mode,
         fract ==1,
          carrying_capacity==20
          ) %>%
  ggplot(aes(x = value, y = attack_round, colour = factor(carrying_capacity))) + 
  geom_point() +
  facet_grid(~metric)

+
  scale_color_viridis_c()



#load strain
strain_df <- c(list.files("/home/jonno/test_strain/IEEE_118_igraph/IEEE_118_igraph", full.names = T) 
               ) %>%
  map_df(~{
    
    elements <- basename(.x) %>% str_remove(pattern = ".rds") %>% str_split(pattern = "_")
    
    edge_embeddings <-read_rds(.x)$edge_embeddings  %>%
      summarise(mean_strain = mean(strain),
                median_strain = median(strain),
                mean_tension = mean(tension),
                median_tension = median(tension)) %>%
      mutate(fract = elements[[1]][2],
             carrying_capacity = elements[[1]][4],
             largest = elements[[1]][6],
             smallest = elements[[1]][8],
             robin_hood_mode = elements[[1]][11])
    
    return(edge_embeddings)
    
  }) %>%
  mutate(
    fract = as.numeric(fract),
    carrying_capacity = as.numeric(carrying_capacity),
         largest = as.numeric(largest),
         smallest = as.numeric(smallest),
         robin_hood_mode = as.logical(robin_hood_mode)) #this needs to be checked when FALSE is present


test <- strain_df  %>%
  filter(carrying_capacity == 20,
         smallest == 0.5,
         largest == 0.1,
         fract == 1,
         robin_hood_mode == T)
  


kappa <- function(value){
  
  (value-min(value))/(max(value)-min(value))
  
}


strain_norm_df <- strain_df %>%
  mutate(#force strain to be relative
  mean_strain = kappa(mean_strain),
                median_strain = kappa(median_strain),
                mean_tension = kappa(mean_tension),
                median_tension = kappa(median_tension)
)

test_strain <- IEEE_118_agg_res %>%
  left_join(strain_norm_df, by = c("carrying_capacity", "smallest", "largest", "fract", "robin_hood_mode")) %>%
  rename(harmonic_alpha = mean_loading) %>%
  filter(!is.na(mean_strain)) %>%
    pivot_longer(., cols = c("harmonic_alpha", "median_loading", "mean_alpha", "mean_tension", "mean_strain", "median_strain",
                             "mean_tension", "median_tension"), 
                 names_to = "metric" ) %>%
  mutate(embeddings = case_when(
    grepl("tension|strain", metric) ~ "embeddings",
    TRUE ~"alpha" 
  ))


test_strain %>%
   filter(
        # fract ==1,
        #  carrying_capacity==20
          ) %>%
  ggplot(aes(x = value, y = attack_round, colour = as.factor(robin_hood_mode))) + 
  geom_point() +
  facet_wrap(~embeddings + metric) +
  labs(colour = "capacity")
+
  geom_smooth()


test_strain %>%
  filter(metric =="harmonic_alpha"
#        carrying_capacity == 5
         ) %>%
  ggplot(aes(x = value, y = attack_round, colour = factor(carrying_capacity))) + 
  geom_point() +
  facet_wrap(~factor(fract)) +
  geom_smooth(se = FALSE)


test2 <- test %>%
   filter(metric !="mean_alpha",
          carrying_capacity==3)

test <- read_rds(.x) %>%
           mutate(file_path = dirname(.x)) %>%
  arrange(-nodes) %>%
  mutate_at(.vars = 5:8, .funs = first) %>%
  mutate(has_gc = mean_degree_sqrd > 2*mean_degree) %>%
  filter(!has_gc) %>%
  slice(1)
  group_by(file_path) %>%
  summarise_all(first) 

  #compare the different metrics in terms of accuracy
  
  multi_metric <- metric_set(rmse, rsq, mae, smape)
  results <-unique(test_strain$metric) %>%
    map_df(~{
      
      temp <- test_strain %>%
        filter(
          !is.na(value),
          fract==1,
          metric ==.x)
      
      loess_mod <- loess(formula =attack_round~ value, 
                         data = temp)
      
      model_comp <- temp  %>%
        mutate(preds = predict(loess_mod)
        )
      
      multi_metric(data = model_comp, truth = attack_round, estimate = preds) %>% 
        mutate(type = .x)
      
    })
  
  
results %>%
  group_by(.metric) %>%
  mutate(estimate =kappa(.estimate)) %>%
  ggplot(aes(x = .metric, y = estimate, colour = type, group = type)) + geom_line() + geom_point()
  
  missing_strain <- IEEE_118_agg_res %>%
    left_join(strain_norm_df, by = c("carrying_capacity", "smallest", "largest", "fract", "robin_hood_mode")) %>%
    rename(harmonic_alpha = mean_loading) %>%
    filter(is.na(mean_strain)) 

  
tar_files <- list.files("/home/jonno/test_strain/IEEE_118/") %>% gsub(".tgz", "",.)
missing_vect <- (list.dirs("/home/jonno/test_strain/IEEE_118") %in% missing_strain$file_path)
  
list.dirs("/home/jonno/HPC_jobs/IEEE_118_igraph/")[missing_vect]


```


##Find missing

```{r}
missing_df <- generate_concentrator_parameters("IEEE_118_igraph") 


missing_attack <- missing_df %>%
  left_join(IEEE_118_results %>% 
              mutate(missing = FALSE) %>% 
              rename(fraction = fract) %>% 
              select(simulation_id:robin_hood_mode, missing)) %>%
  filter(is.na(missing)) %>%
  mutate(missing = TRUE)
#only missing from two groups this is clearly a timing issue
table(missing_attack$compute_group)

missing_strain <- missing_df %>%
  filter(simulation_id ==1) %>%
  left_join(strain_df %>%  
              mutate(missing = FALSE) %>% 
              rename(fraction = fract) %>% 
              select(fraction:robin_hood_mode, missing)) %>%
  filter(is.na(missing)) %>%
  mutate(compute_group_strain_2 = 1:n()) %>%
  select(embeddings_path, 
          #compute_group_strain,
         compute_group_strain_2
         )
  
saveRDS(missing_strain, file.path(project_folder, "missing_files", "strain_concentrator.rds"))




```


```{r}
IEEE_14_igraph]$ ~/Spring_Embeddings_Paper/bash_script_concentrator/qsub_custom IEEE_14_igraph attack 01:00:00

load_file <- "IEEE_118_igraph"
task_id <- 1

#untar specific file
tar -xzf files_from_job_2101622.99.tgz -C ~/Scratch/attack_out --wildcards --no-anchored '*collapse_summaries*' --strip-components 4

#untar all files and move them to a new folder. All the files are collected in the final folder structure which is very helpful
for f in *.tgz; do tar -xzf $f -C ~/Scratch/attack_out --wildcards --no-anchored '*collapse_summaries*' --strip-components 4; done

tar -czvf IEEE_118.tgz /IEEE_118

#use rsync to get the files off

list.files( "/home/jonno/test_strain/IEEE_118", pattern = ".tgz") %>%
  walk(~{
    
    untar_myriad_strain_files(tar_path = "/home/jonno/test_strain/IEEE_118", 
                              tar_file = .x, 
                              extraction_directory = "/home/jonno/test_strain/Extracted_118")
    
    
  })
  

```

#